---
title: "Is there motor activity?"
author: "Brooke Staveland"
date: "6/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 12,  # set default width of figures
  fig.height <- 6,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- TRUE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(beepr)
library(stringr)
library(lmtest)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_tf_wave_data.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "load_all_freq_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "run_permuted_regressions.R"))
source(path(here(), "R", "compile_results.R"))
source(path(here(), "R", "run_filtered_anova.R"))
source(path(here(), "R", "merge_stepped_anova_results.R"))
source(path(here(), "R", 'mutate_cond.R'))

## plotting helpers ##
# ggthemr("solarized")

# ## paralellization ##
# nCores <- 2
# registerDoParallel(nCores)

```


This file is looking for evidence of motor activity during our task, as a sanity check for our preprocessing scripts. We have two different preprocessing methods, one specific to high frequency activity that uses the hilbert transform, and the other across all frequency bands that uses wavelets.

The subject for which we have motor electrodes is `IR19`, who responded to the task bilaterally, where the key pressed with the left hand signaled the left option was chosen, and vice versa for the right hand. The electrodes we have are all left hemisphere electrodes.

```{r load-elec-locations}

# load data #
elec_locations <- read.csv(path(here(), "munge", "combined_electrode_info_cleaned.csv"))

# filter and print via kable #
motor_elecs <- elec_locations %>%
  filter(subject == "CP34") %>%
  filter(str_detect(`Loc.Meeting`, "M1|motor|Motor")) %>%
  select(Electrode, `Loc.Meeting`)

kable(motor_elecs) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
  

```


```{r behave-prep}

# path to beahvioral files #
path_to_raw_behave <- fs::path(here(), "../dg_behave_formatted")
path_to_behave_munge <- fs::path(here(), "munge", "combined_behavioral_data.csv")
path_to_behave_clean <- fs::path(here(), "munge", "clean_behavioral_data.csv")

# concactenate behavioral data #
load_behave_data(path_to_raw_behave)

# prep behavioral data #
prep_behave_data(path_to_behave_munge)

# load clean data #
behave_data <- read.csv(path_to_behave_clean)

# filter to current subject #
behave_data_08 <- behave_data %>% filter(SID == "DG_s08")
behave_data_11 <- behave_data %>% filter(SID == "DG_s11")
behave_data_12 <- behave_data %>% filter(SID == "DG_s12")
behave_data_06 <- behave_data %>% filter(SID == "DG_s06")
behave_data_13 <- behave_data %>% filter(SID == "DG_s13")
behave_data_14 <- behave_data %>% filter(SID == "DG_s14")

# table(behave_data$ineq_advent_choice)
# table(behave_data_08$ineq_disadvent_choice)
# table(behave_data_11$ineq_disadvent_choice)
# table(behave_data_12$ineq_disadvent_choice)
```


### Hilbert Method

This method replicates the methods in Saez 2018, and was only used to get the high frequency activity.

```{r load-raw-hfa-hilbert-data}

# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_new.csv")
file_path_to_hg_data <- path(here(), "munge", "savio_cluster", "CP34-1_hfa_munge_presentation_locked_new.csv")

# load data #
hg_data <- load_high_gamma_data(file_path_to_hg_data, file_path_to_electrode_names)
elecs_to_use <- motor_elecs

# add behavioral data, remove bad trials, remove behavioral data again #
hg_data <- merge.data.frame(hg_data, behave_data_14, by.x = "trial", by.y = "round", all.x = T, all.y = F)
hg_data <- hg_data %>% filter(!is.na(RT)) %>% filter(RT < 2)

# filter to motor electrodes #
hg_data <- hg_data %>% filter(grepl(paste(elecs_to_use$Electrode, collapse = "|"), electrodes))

# get the baseline #
baseline_df <- hg_data %>% select(1:200)
baseline <- apply(baseline_df, 1, function(x) mean(x, na.rm = T))

# subtract baseline #
hg_data[, grepl("time_", colnames(hg_data))] <- apply(hg_data[, grepl("time_", colnames(hg_data))], 2, function(col) t(as.vector(col - baseline)))
       
```

```{r load-raw-beta-hilbert-data}

# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_new.csv")
file_path_to_beta_data <- path(here(), "munge", "savio_cluster", "CP34-1_beta_munge_presentation_locked_new.csv")

# load data #
beta_data <- load_high_gamma_data(file_path_to_beta_data, file_path_to_electrode_names)
elecs_to_use <- motor_elecs

# add behavioral data, remove bad trials, remove behavioral data again #
beta_data <- merge.data.frame(beta_data, behave_data_14, by.x = "trial", by.y = "round", all.x = T, all.y = F)
beta_data <- beta_data %>% filter(!is.na(RT)) %>% filter(RT < 2)

# filter to motor electrodes #
beta_data <- beta_data %>% filter(grepl(paste(elecs_to_use$Electrode, collapse = "|"), electrodes))

# get the baseline #
baseline_df <- beta_data %>% select(1:200)
baseline <- apply(baseline_df, 1, function(x) mean(x, na.rm = T))

# subtract baseline #
beta_data[, grepl("time_", colnames(beta_data))] <- apply(beta_data[, grepl("time_", colnames(beta_data))], 2, function(col) t(as.vector(col - baseline)))
       
```
*Raw Hilbert HFA Activity*

Below are the four electrode pairs RT-sorted high frequency activity plots. `0` is presentation time, and the average  of 200ms of activity before presentation was subtracted from all subsequent points.

```{r plot-raw-hilbert-data}

hilbert_raw_plots <- function(elec, df) {
  df %>%
    filter(electrodes == elec) %>%
    arrange(desc(RT)) %>%
    mutate(trial = factor(trial, levels = trial)) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    mutate(time = (as.numeric(gsub("time_", "", time)) - 200)) %>%
    ggplot(., aes(x = time, y = trial, color = power, fill = power)) +
    geom_tile() + 
    geom_point(aes(y = trial, x = RT*1000), color = "white", size = 1) +
    geom_vline(xintercept = 0, color = "white") +
    theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
    scale_fill_viridis(limits = c(-6, 6), begin = 0, end = 1)   +
    scale_color_viridis(limits = c(-6, 6), begin = 0, end = 1) +
    ggtitle(paste0(elec))
}

```

### Raw HFA Data
```{r plot-raw-hfa}

hfa_list <- as.list(as.character(unique(hg_data$electrodes)))

lapply(plot_list, function(x) hilbert_raw_plots(x, hg_data))

```

### Raw Beta Data

```{r plot-raw-hfa}

beta_list <- as.list(as.character(unique(beta_data$electrodes)))


lapply(plot_list, function(x) hilbert_raw_plots(x, beta_data))

```

```{r hfa-envelope}

hilbert_enevelope_plots <- function(elec, df) {
df %>%
    filter(electrodes == elec) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    group_by(RT) %>%
    mutate(time = round(((as.numeric(gsub("time_", "", time)) - (RT*1000)) - 200))) %>%
    ungroup() %>%
    # mutate(time_factor = as.factor(time)) %>%
    group_by(time) %>%
    mutate(average_power = mean(power, na.rm = T)) %>%
    distinct(time, average_power) %>%
    ggplot(., aes(x = time, y = average_power)) +
    geom_line() + 
    # theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
    # scale_fill_viridis(limits = c(-5, 5), begin = 0, end = 1)   +
    # scale_color_viridis(limits = c(-5, 5), begin = 0, end = 1) +
    theme_bw() +
    ggtitle(paste0(elec))
}


```


###  HFA Envelopes
```{r plot-raw-hfa}

hfa_list <- as.list(as.character(unique(hg_data$electrodes)))

lapply(plot_list, function(x) hilbert_raw_plots(x, hg_data))

```

### Beta Envelopes

```{r plot-raw-hfa}

beta_list <- as.list(as.character(unique(beta_data$electrodes)))


lapply(plot_list, function(x) hilbert_enevelope_plots(x, beta_data))

```


*Raw Hilbert HFA Activity - split by side chosen*

This is the same data as the foru plots above, but split by side chosen. It is a little difficult to see, but I don't think there is any striking difference between the two.


```{r plot-raw-hilbert-data-split}

left_right_raw_plots <- function(elec) {
  hg_data %>%
    filter(electrodes == elec) %>%
    arrange(desc(RT)) %>%
    mutate(trial = factor(trial, levels = trial)) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    mutate(time = (as.numeric(gsub("time_", "", time)) - 200)) %>%
    ggplot(., aes(x = time, y = trial, color = power, fill = power)) +
    geom_tile() + 
    geom_point(aes(y = trial, x = RT*1000), color = "black", size = 1) +
    geom_vline(xintercept = 0, color = "white") +
    theme_bw() +
    theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), 
          strip.background = element_rect(fill = "white", color = "black")) + 
    theme(panel.border = element_rect(colour = "black"), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
    scale_fill_viridis(limits = c(-3, 3), begin = 0, end = 1)   +
    scale_color_viridis(limits = c(-3, 3), begin = 0, end = 1) +
    facet_wrap(~side_chosen) +
    ggtitle(paste0(elec))
}

lapply(plot_list, function(x) left_right_raw_plots(x))

```

### Wavlet method

This is an alternative way of calculating the hfa, using wavelets, and is based on scripts from Anais and Ludo. We also have all the lower frequencies from this method. Some important differences to note are 1) the wavelet method sampled the data every 50ms, while the hilbert method sampled every 1ms and 2) the hilbert data is z-scored while the wavelet data was log transformed. 


```{r load-all-freq-data}

# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "IR19_electrodes_presentation_TFwaves.csv")
file_path_to_tf_data <- path(here(), "munge", "IR19_all_frequencies_munge_presentation_locked_extended.csv")

# load data #
tf_data <- load_all_freq_data(file_path_to_tf_data, file_path_to_electrode_names)
elecs_to_use <- motor_elecs

# get the baseline #
baseline_df <- tf_data %>% select(1:4)
baseline <- apply(baseline_df, 1, function(x) mean(log(x), na.rm = T))

# subtract baseline #
tf_data[, grepl("time_", colnames(tf_data))] <- apply(tf_data[, grepl("time_", colnames(tf_data))], 2, function(col) t(as.vector(log(col) - baseline)))
       
# add behavioral data, remove bad trials, remove behavioral data again #
tf_data <- merge.data.frame(tf_data, behave_data_08, by.x = "trial", by.y = "round", all.x = T, all.y = F)
tf_data <- tf_data %>% filter(!is.na(RT))

# filter to motor electrodes #
tf_data <- tf_data %>% filter(grepl(paste(elecs_to_use$Electrode, collapse = "|"), electrodes))

# filter out first two trials #
tf_data <- tf_data %>% filter(!trial %in% c(1, 2))

```

*Time-frequency plots*

The four plots below show the time-frequency power spectrum, averaged over all trials. There does seem to be some dynamics, especially in the second plot. Not sure if it is still underwhelming though, given its M1. 

```{r plot-time-freq}
# freqs <- sort(unique(hold$data$frequency))
# weights <- sort(rgamma(length(freqs), 1, .5), decreasing = T)
# filter_freq <- sample(freqs, length(freqs), replace = T, prob = weights)

plot_time_freq_plots <- function(elec) {
tf_data %>%
  filter(electrodes == elec) %>%
  # filter(frequency %in% exp(pretty(log(freqs), 20))) %>%
  gather(key = "time", value = "power", starts_with("time")) %>%
  group_by(frequency, time) %>%
  mutate(average_power = mean(power, na.rm = T)) %>%
  ungroup() %>%
  mutate(time = (as.numeric(gsub("time_", "", time)) - 4) * 50) %>%
  mutate(frequency = log(frequency)) %>%
  arrange(desc(frequency)) %>%
  mutate(freq_height = sort(frequency * .2)) %>%
  ggplot(., aes(x = time, y = frequency, color = average_power, fill = average_power)) +
  geom_tile(alpha = .7, aes(height = freq_height)) + 
  geom_vline(xintercept = 0, color = "white") +
  theme(panel.background = element_rect(fill = "white")) +
  scale_y_continuous(breaks = 0:5, labels = c(0, floor(exp(1:5))) )+
  # scale_y_log10() +
  scale_fill_viridis(limits = c(-1.2, 1), begin = 0, end = 1)   +
  scale_color_viridis(limits = c(-1.2, 1), begin = 0, end = 1) +
  ggtitle(paste0(elec))
  
}

lapply(plot_list, function(x) plot_time_freq_plots(x))

```


*Raw Wavelet HFA RT-sorted plots*

These are the same type of plots as in the begining of the doc, but with the wavelet data instead of the hilbert data. We were looking for similarity, but it is a little difficult to compare them, given the differences in transformation/averaging.

```{r load-hg-wave-data}

# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "IR19_electrodes_presentation_TFwaves.csv")
file_path_to_tf_data <- path(here(), "munge", "IR19_low-70_high-200_munge_presentation_locked_extended.csv")

# load data #
hg_tf_data <- load_tf_wave_data(file_path_to_tf_data, file_path_to_electrode_names)
elecs_to_use <- motor_elecs

# get the baseline #
baseline_df <- hg_tf_data %>% select(1:4)
baseline <- apply(baseline_df, 1, function(x) mean(log(x), na.rm = T))

# subtract baseline #
hg_tf_data[, grepl("time_", colnames(hg_tf_data))] <- apply(hg_tf_data[, grepl("time_", colnames(hg_tf_data))], 2, function(col) t(as.vector(log(col) - baseline)))
       
# add behavioral data, remove bad trials, remove behavioral data again #
hg_tf_data <- merge.data.frame(hg_tf_data, behave_data_08, by.x = "trial", by.y = "round", all.x = T, all.y = F)
hg_tf_data <- hg_tf_data %>% filter(!is.na(RT))

# filter to motor electrodes #
hg_tf_data <- hg_tf_data %>% filter(grepl(paste(elecs_to_use$Electrode, collapse = "|"), electrodes))

# filter out first two trials #
hg_tf_data <- hg_tf_data %>% filter(!trial %in% c(1, 2))

```



```{r plot-raw-wavelet-data}
plot_list <- as.list(as.character(unique(hg_data$electrodes)))

wavelet_raw_plots <- function(elec) {
  hg_tf_data %>%
    filter(electrodes == elec) %>%
    arrange(desc(RT)) %>%
    mutate(trial = factor(trial, levels = trial)) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    mutate(time = (as.numeric(gsub("time_", "", time)) - 4) * 50) %>%
    ggplot(., aes(x = time, y = trial, color = power, fill = power)) +
    geom_tile() + 
    geom_point(aes(y = trial, x = RT*1000), color = "black", size = 1) +
    geom_vline(xintercept = 0, color = "white") +
    theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
    scale_fill_viridis(limits = c(-3, 3), begin = 0, end = 1)   +
    scale_color_viridis(limits = c(-3, 3), begin = 0, end = 1) +
    ggtitle(paste0(elec))
}

lapply(plot_list, function(x) wavelet_raw_plots(x))

```

