---
title: "Is there motor activity?"
author: "Brooke Staveland"
date: "6/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 12,  # set default width of figures
  fig.height <- 6,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- TRUE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(beepr)
library(stringr)
library(lmtest)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_tf_wave_data.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "load_all_freq_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "run_permuted_regressions.R"))
source(path(here(), "R", "compile_results.R"))
source(path(here(), "R", "run_filtered_anova.R"))
source(path(here(), "R", "merge_stepped_anova_results.R"))
source(path(here(), "R", 'mutate_cond.R'))

## plotting helpers ##
# ggthemr("solarized")

# ## paralellization ##
# nCores <- 2
# registerDoParallel(nCores)

```


This file is looking for evidence of motor activity during our task, as a sanity check for our preprocessing scripts. I am looking at different methods of standardization, since our first pass did not have much stereotyped activity.

The subject for which we have grid motor electrodes is `CP34`, who responded to the task bilaterally, where the key pressed with the left hand signaled the left option was chosen, and vice versa for the right hand. 

```{r load-elec-locations}

# load data #
elec_locations <- read.csv(path(here(), "munge", "combined_electrode_info_cleaned.csv"))

# filter and print via kable #
motor_elecs <- elec_locations %>%
  filter(subject %in% c("CP34", "IR19")) %>%
  filter(str_detect(`Loc.Meeting`, "M1|motor|Motor|Precentral")) %>%
  select(Electrode, `Loc.Meeting`, subject)

kable(motor_elecs) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
  

```


```{r behave-prep}

# path to beahvioral files #
path_to_raw_behave <- fs::path(here(), "../dg_behave_formatted")
path_to_behave_munge <- fs::path(here(), "munge", "combined_behavioral_data.csv")
path_to_behave_clean <- fs::path(here(), "munge", "clean_behavioral_data.csv")

# concactenate behavioral data #
load_behave_data(path_to_raw_behave)

# prep behavioral data #
prep_behave_data(path_to_behave_munge)

# load clean data #
behave_data <- read.csv(path_to_behave_clean)

# filter to current subject #
behave_data_08 <- behave_data %>% filter(SID == "DG_s08")
behave_data_11 <- behave_data %>% filter(SID == "DG_s11")
behave_data_12 <- behave_data %>% filter(SID == "DG_s12")
behave_data_06 <- behave_data %>% filter(SID == "DG_s06")
behave_data_13 <- behave_data %>% filter(SID == "DG_s13")
behave_data_14 <- behave_data %>% filter(SID == "DG_s14")

# table(behave_data$ineq_advent_choice)
# table(behave_data_08$ineq_disadvent_choice)
# table(behave_data_11$ineq_disadvent_choice)
# table(behave_data_12$ineq_disadvent_choice)
```

```{r load-data-functions}

load_power_data <- function(file_path_to_power_data, file_path_to_electrode_names, behave_data) {
  # load data #
  power_data <- load_high_gamma_data(file_path_to_power_data, file_path_to_electrode_names)
  elecs_to_use <- motor_elecs
  
  # add behavioral data, remove bad trials, remove behavioral data again #
  power_data <- merge.data.frame(power_data, behave_data, by.x = "trial", by.y = "round", all.x = T, all.y = F)
  power_data <- power_data %>% filter(!is.na(RT)) %>% filter(RT < 2)
  
  # filter to motor electrodes #
  power_data <- power_data %>% filter(grepl(paste(elecs_to_use$Electrode, collapse = "|"), electrodes))
  
  # get the baseline #
  baseline_df <- power_data %>% select(1:200)
  baseline <- apply(baseline_df, 1, function(x) mean(x, na.rm = T))
  
  # subtract baseline #
  power_data[, grepl("time_", colnames(power_data))] <- apply(power_data[, grepl("time_", colnames(power_data))], 2, function(col) t(as.vector(col - baseline)))

  return(power_data)
}
```

```{r plotting-functions}

ggthemr::ggthemr("pale", layout = "plain")
getPalette = colorRampPalette(brewer.pal(10, "Set1"))


hilbert_raw_plots <- function(elec, df, min_val, max_val) {
  df %>%
    filter(electrodes == elec) %>%
    arrange(desc(RT)) %>%
    mutate(trial = factor(trial, levels = trial)) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    mutate(time = (as.numeric(gsub("time_", "", time)) - 200)) %>%
    ggplot(., aes(x = time, y = trial, color = power, fill = power)) +
    geom_tile() + 
    geom_point(aes(y = trial, x = RT*1000), color = "white", size = 1) +
    geom_vline(xintercept = 0, color = "white") +
    # theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
    scale_fill_viridis(begin = 0, end = 1, option = "A") +
    scale_color_viridis(begin = 0, end = 1, option = "A") +
    # scale_fill_viridis(limits = c(min_val, max_val), begin = 0, end = 1, option = "A")   +
    # scale_color_viridis(limits = c(min_val, max_val), begin = 0, end = 1, option = "A") +
    ggtitle(paste0(elec))
}

hilbert_enevelope_plots <- function(elec, df) {
df %>%
    filter(electrodes == elec) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    mutate(time = as.numeric(gsub("time_", "", time))) %>%
    mutate(time_choice = time - (RT*1000) - 200) %>%
    filter(time_choice > RT*-1000) %>%
    mutate(time_bins = cut(time_choice, seq(min(time_choice), max(time_choice), 1), labels = F)) %>%
    mutate(time_bins = factor(time_bins, labels = seq(min(time_choice), (max(time_choice) -1), 1))) %>%
    group_by(time_bins, stand_method) %>%
    add_tally() %>%
    filter(n > 5) %>%
    mutate(average_power = mean(power, na.rm = T)) %>%
    distinct(time, average_power) %>%
    mutate(time_plot = as.numeric(levels(time_bins)[time_bins])) %>%
    ggplot(., aes(x = time_plot, y = average_power, color = stand_method)) +
    theme_bw() +
    geom_line() + 
    scale_color_manual(values = wes_palette("Darjeeling1")) +
    ggtitle(paste0(elec))
}

hilbert_enevelope_plots_side <- function(elec, df) {
df %>%
    filter(electrodes == elec) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    mutate(time = as.numeric(gsub("time_", "", time))) %>%
    mutate(time_choice = time - (RT*1000) - 200) %>%
    filter(time_choice > RT*-1000) %>%
    mutate(time_bins = cut(time_choice, seq(min(time_choice), max(time_choice), 1), labels = F)) %>%
    mutate(time_bins = factor(time_bins, labels = seq(min(time_choice), (max(time_choice) -1), 1))) %>%
    group_by(time_bins, stand_method, side_chosen) %>%
    add_tally() %>%
    filter(n > 5) %>%
    mutate(average_power = mean(power, na.rm = T)) %>%
    distinct(time, average_power) %>%
    mutate(time_plot = as.numeric(levels(time_bins)[time_bins])) %>%
    ggplot(., aes(x = time_plot, y = average_power, color = stand_method)) +
    theme_bw() +
    geom_line() + 
    scale_color_manual(values = wes_palette("Darjeeling1")) +
    facet_wrap(~side_chosen) +
    ggtitle(paste0(elec))
}

hilbert_enevelope_plots_pres <- function(elec, df) {
df %>%
    filter(electrodes == elec) %>%
    gather(key = "time", value = "power", starts_with("time")) %>%
    group_by(RT) %>%
    mutate(time = ((as.numeric(gsub("time_", "", time)) - 200))) %>%
    filter(time > 0) %>%
    ungroup() %>%
    # mutate(time_factor = as.factor(time)) %>%
    group_by(time, stand_method) %>%
    mutate(average_power = mean(power, na.rm = T)) %>%
    distinct(time, average_power) %>%
    ggplot(., aes(x = time, y = average_power, color = stand_method)) +
    geom_line() + 
    scale_color_manual(values = wes_palette("Darjeeling1")) +
    ggtitle(paste0(elec))
}

```



## Beta Power

First, I am looking within the beta band, `13-30Hz`, calculated with the hilbert method. 

```{r load-raw-beta-hilbert-data}

## zscore each trial ##
# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_zscore.csv")
file_path_to_beta_data <- path(here(), "munge", "savio_cluster", "CP34-1_beta_munge_presentation_locked_zscore.csv")
# Load it #
beta_zscore <- load_power_data(file_path_to_beta_data, file_path_to_electrode_names, behave_data_14)
beta_zscore$stand_method <- "zscore"


## zscore over all task ##
# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_zscore_over_all.csv")
file_path_to_beta_data <- path(here(), "munge", "savio_cluster", "CP34-1_beta_munge_presentation_locked_zscore_over_all.csv")
# Load it #
beta_zscore_all <- load_power_data(file_path_to_beta_data, file_path_to_electrode_names, behave_data_14)
beta_zscore_all$stand_method <- "zscore_all"



## robustScaler each trial ##
# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_new.csv")
file_path_to_beta_data <- path(here(), "munge", "savio_cluster", "CP34-1_beta_munge_presentation_locked_new.csv")
# Load it #
beta_rscaler <- load_power_data(file_path_to_beta_data, file_path_to_electrode_names, behave_data_14)
beta_rscaler$stand_method <- "rscaler"


## robustScaler each trial ##
# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_rscaler_2575.csv")
file_path_to_beta_data <- path(here(), "munge", "savio_cluster", "CP34-1_beta_munge_presentation_locked_rscaler_2575.csv")
# Load it #
beta_rscaler25 <- load_power_data(file_path_to_beta_data, file_path_to_electrode_names, behave_data_14)
beta_rscaler25$stand_method <- "rscaler25"


## robustScaler over all task ##
# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_rsacler_over_all.csv")
file_path_to_beta_data <- path(here(), "munge", "savio_cluster", "CP34-1_beta_munge_presentation_locked_rsacler_over_all.csv")
# Load it #
beta_rscaler_all <- load_power_data(file_path_to_beta_data, file_path_to_electrode_names, behave_data_14)
beta_rscaler_all$stand_method <- "rscaler_all"

beta_data <- rbind(beta_zscore, beta_rscaler, beta_rscaler25)
```

```{r load-IR19-data}

file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "IR19_electrodes_presentation_locked_zscore.csv")
file_path_to_beta_data <- path(here(), "munge", "savio_cluster", "IR19_beta_munge_presentation_locked_zscore.csv")
# Load it #
cp34_zscore <- load_power_data(file_path_to_beta_data, file_path_to_electrode_names, behave_data_08)
cp34_zscore$stand_method <- "zscore"


```

### Beta Envelopes CP34

```{r plot-raw-hfa-cp34}

beta_list <- as.list(as.character(unique(beta_data$electrodes)))


lapply(beta_list, function(x) hilbert_enevelope_plots(x, beta_data))


lapply(beta_list, function(x) hilbert_enevelope_plots_side(x, beta_data))

```

### Raw Beta Data CP34

```{r plot-raw-beta-cp34}

beta_list <- as.list(as.character(unique(beta_rscaler25$electrodes)))
beta_list <- as.list("G47")

lapply(beta_list, function(x) hilbert_raw_plots(x, beta_rscaler25, 2, 5))
lapply(beta_list, function(x) hilbert_raw_plots(x, beta_rscaler, 2, 5))
lapply(beta_list, function(x) hilbert_raw_plots(x, beta_zscore, 2, 5))



```
```{r outliers}

elec_47 <- beta_rscaler25 %>%
  filter(electrodes == "G47") %>%
  gather(key = "time", value = "power", starts_with("time")) %>%
  select(time, power, trial) %>%
  group_by(trial) %>%
  summarise(mean = mean(power), min = min(power), max = max(power)) %>%
  arrange(mean) 

elec_47 %>%
  kable() %>%
  kable_styling()

beta_rscaler25 %>%
  gather(key = "time", value = "power", starts_with("time")) %>%
  select(time, power, trial) %>%
  group_by(trial) %>%
  summarise(mean = mean(power), min = min(power), max = max(power)) %>%
  gather(key = "metric", value = "power", -trial) %>%
  ggplot(., aes(x = trial, y = power, color = metric)) +
  geom_point() +
  scale_color_manual(values = wes_palette("Darjeeling1")) +
  theme_bw()

```


### Presentationa and Choice Envelopes IR19
```{r plot-raw-beta-ir19}

cp34_beta_list <- as.list(as.character(unique(cp34_zscore$electrodes)))

hilbert_enevelope_plots_pres
lapply(cp34_beta_list, function(x) hilbert_enevelope_plots(x, cp34_zscore))
lapply(cp34_beta_list, function(x) hilbert_enevelope_plots_pres(x, cp34_zscore))

```

### Raw Beta IR19

```{r plot-raw-hfa-ir19}

beta_list <- as.list(as.character(unique(cp34_zscore$electrodes)))

lapply(beta_list, function(x) hilbert_raw_plots(x, cp34_zscore, -4, 8))

```


### High Frequency Activity

Next, I looked within the hfa band, `70-150Hz`, calculated with the hilbert method with a multitaper as follows: `[70 90; 80 100; 90 110; 100 120; 110 130; 120 140; 130 150];`


```{r load-raw-hfa-hilbert-data}

# ## zscore each trial ##
# # necessary paths #
# file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_zscore.csv")
# file_path_to_hfa_data <- path(here(), "munge", "savio_cluster", "CP34-1_hfa_munge_presentation_locked_zscore.csv")
# # Load it #
# hfa_zscore <- load_power_data(file_path_to_hfa_data, file_path_to_electrode_names)
# hfa_zscore$stand_method <- "zscore"


## zscore over all task ##
# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_zscore_over_all.csv")
file_path_to_hfa_data <- path(here(), "munge", "savio_cluster", "CP34-1_hfa_munge_presentation_locked_zscore_over_all.csv")
# Load it #
hfa_zscore_all <- load_power_data(file_path_to_hfa_data, file_path_to_electrode_names, behave_data_14)
hfa_zscore_all$stand_method <- "zscore_all"



# ## robustScaler each trial ##
# # necessary paths #
# file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_new.csv")
# file_path_to_hfa_data <- path(here(), "munge", "savio_cluster", "CP34-1_hfa_munge_presentation_locked_new.csv")
# # Load it #
# hfa_rscaler <- load_power_data(file_path_to_hfa_data, file_path_to_electrode_names)
# hfa_rscaler$stand_method <- "rscaler"


## robustScaler over all task ##
# necessary paths #
file_path_to_electrode_names <- path(here(), "munge", "savio_cluster", "CP34-1_electrodes_presentation_locked_rsacler_over_all.csv")
file_path_to_hfa_data <- path(here(), "munge", "savio_cluster", "CP34-1_hfa_munge_presentation_locked_rsacler_over_all.csv")
# Load it #
hfa_rscaler_all <- load_power_data(file_path_to_hfa_data, file_path_to_electrode_names, behave_data_14)
hfa_rscaler_all$stand_method <- "rscaler_all"

hfa_data <- rbind(hfa_zscore_all, hfa_rscaler_all)
```


###  HFA Envelopes
```{r plot-env-hfa}

hfa_list <- as.list(as.character(unique(hfa_zscore_all$electrodes)))

lapply(hfa_list, function(x) hilbert_enevelope_plots(x, hfa_zscore_all))

```



### Raw HFA Data
```{r plot-raw-hfa-z}

hfa_list <- as.list(as.character(unique(hfa_zscore_all$electrodes)))

lapply(hfa_list, function(x) hilbert_raw_plots(x, hfa_zscore_all))

```

*Raw Hilbert HFA Activity - split by side chosen*

This is the same data as the foru plots above, but split by side chosen. It is a little difficult to see, but I don't think there is any striking difference between the two.

