---
title: "Dictator Paper Behavioral Analysis"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 12,  # set default width of figures
  fig.height <- 6,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- TRUE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(janitor)
library(extrafont)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "compile_results.R"))
# source('~/Projects/nice_r_functions/ggpaired_pretty.R')
source(path(here(), "R", 'mutate_cond.R'))

## plotting helpers ##
ggthemr("solarized")
solarized_palette <- c(
        '#073642', '#E1965D',
        '#268bd2', '#dc322f',
        '#2aa198', '#b58900',
       '#6c71c4', '#d33682')

getPalette = colorRampPalette(brewer.pal(12, "Set1"))

# ## parallelization ##
# nCores <- 4
# registerDoParallel(nCores)

```

# Behavioral analyses


This notebook focus on the behavioral analyses, as well as creates the panels for Figure 1, and Supplemental Figures 1 and 2, and Supplemental Table 1.


### Load and Clean Data

```{r behave-prep, echo = T}

# path to beahvioral files #
path_to_raw_behave <- fs::path(here(), "../dg_behave_formatted")
path_to_behave_munge <- fs::path(here(), "munge", "combined_behavioral_data.csv")
path_to_behave_clean <- fs::path(here(), "munge", "clean_behavioral_data.csv")

# concactenate behavioral data #
load_behave_data(path_to_raw_behave)

# prep behavioral data #
prep_behave_data(path_to_behave_munge)

# load clean data #
behave_data <- read.csv(path_to_behave_clean)

```


### SID Renaming

Original student to work on the data used SIDs specific to the dictator task. However, as I continued the analyses I kept running into problems when joining with the brain data where I could accidentally match the wrong behavioral file to the neuro data by inputting the wrong dictator sepcific ID. To avoid this, I changed all the behavioral files to include the neuro data identifier and use that in the rest of the repo, basically ignoring the original dictator SIDs. Saved me a lot of anxiety.

```{r sid-renaming, echo = T}

# filter out each subject, rename using correct IDs#

behave_data_gp51 <- behave_data %>% filter(SID == "DG_s02") %>% mutate(sub = "GP51")
behave_data_19 <- behave_data %>% filter(SID == "DG_s08") %>% mutate(sub = "IR19")
behave_data_35 <- behave_data %>% filter(SID == "DG_s11") %>% mutate(sub = "IR35")
behave_data_28 <- behave_data %>% filter(SID == "DG_s10") %>% mutate(sub = "IR28")
behave_data_39 <- behave_data %>% filter(SID == "DG_s12") %>% mutate(sub = "IR39")
behave_data_16 <- behave_data %>% filter(SID == "DG_s06") %>% mutate(sub = "IR16")
behave_data_10 <- behave_data %>% filter(SID == "DG_s04") %>% mutate(sub = "IR10")
behave_data_57 <- behave_data %>% filter(SID == "DG_s13") %>% mutate(sub = "IR57")
behave_data_26 <- behave_data %>% filter(SID == "DG_s09") %>% mutate(sub = "IR26")
behave_data_09 <- behave_data %>% filter(SID == "DG_s03") %>% mutate(sub = "IR9")
behave_data_cp34 <- behave_data %>% filter(SID == "DG_s14") %>% mutate(sub = "CP34")
behave_data_da8 <- behave_data %>% filter(SID == "DG_s15") %>% mutate(sub = "DA8")
behave_data_da9 <- behave_data %>% filter(SID == "DG_s17") %>% mutate(sub = "DA9")
behave_data_cp38 <- behave_data %>% filter(SID == "DG_s16") %>% mutate(sub = "CP38")
behave_data_st40 <- behave_data %>% filter(SID == "DG_s01") %>% mutate(sub = "ST40")

behave_data_short <- rbind(behave_data_gp51,
                           behave_data_10, 
                           behave_data_16, 
                           behave_data_19, 
                           behave_data_28, 
                           behave_data_35, 
                           behave_data_39, 
                           behave_data_57, 
                           behave_data_09, 
                           behave_data_26, 
                           behave_data_cp34, 
                           behave_data_da8, 
                           behave_data_da9, 
                           behave_data_cp38, 
                           behave_data_st40)
```

### Correlation between variables

```{r behavioral-correlations}

# Examine Correlation between variables, create Supplemental Figure 1 #

task_design_data <- read_csv('../../../task_design_offered_values.csv')

behave_correl_data <- task_design_data %>%
  group_by(Trial) %>%
  mutate(self_var_payoff = if_else(L.self == 10 & L.other == 10, R.self, L.self)) %>%
  mutate(other_var_payoff = if_else(L.self == 10 & L.other == 10, R.other, L.other)) %>%
  mutate(max = max(self_var_payoff, other_var_payoff)) %>%
  mutate(min = min(self_var_payoff, other_var_payoff)) %>%
  mutate(ineq_var_abs = abs(self_var_payoff - other_var_payoff)) %>%
  mutate(ineq_var = self_var_payoff - other_var_payoff) %>%
  ungroup() %>%
  select(self_var_payoff, other_var_payoff, max, min, ineq_var_abs, ineq_var) %>%
  rename(`Self Offer` = self_var_payoff, `Other Offer` = other_var_payoff, Max = max, Min = min, `Signed Inequity` = ineq_var_abs, `Unsigned Inequity` = ineq_var)

catch_trials_df <- behave_correl_data %>%
  filter(`Self Offer` == `Other Offer`)


behavioral_cor <- cor(behave_correl_data, method = "pearson")

task_variable_correlations <- ggcorrplot(behavioral_cor,
           lab = T,
           type = "lower") +
  theme(legend.position = "top", panel.background = element_rect(fill = "white"), 
        plot.background = element_rect(fill = "white", color = "white"),
        plot.title = element_text(hjust = .5)) +
  ggtitle("Correlations between Task Variables")

ggsave(filename = path(here(), "figures", "paper", "task_variable_correlations.tif"),
     device = "tiff",
     width = 6,
     height = 6,
     units = "in",
     dpi = 300,
     plot =  task_variable_correlations)

```

## Descriptive stats for offers and choices

```{r equitable-porbabilites}

ten_ten_df <- behave_data_short %>%
  filter(trial_type != "equality") %>%
  filter(sub %in% ofc_subs) %>%
  filter(!is.na(RT)) %>%
  select(sub, chose_equality, round, trial_type, trial_type) %>%
  distinct() %>%
  mutate(ten_ten = if_else(chose_equality == "10-10", 1, 0)) %>%
  group_by(sub) %>%
  mutate(num_of_trials = n()) %>%
  mutate(num_ten_ten = sum(ten_ten)) %>%
  mutate(percent_equitable = num_ten_ten/num_of_trials) %>%
  select(sub, num_ten_ten, num_of_trials, percent_equitable) %>%
  distinct() %>%
  ungroup() %>%
  mutate(mean_equitable = mean(percent_equitable)) %>%
  mutate(sd_equitable = sd(percent_equitable)) %>%
  mutate(max_equitable = max(percent_equitable)) %>%
  mutate(min_equitable = min(percent_equitable))


# get % time chose equitable on dis trials only #
dis_choice <- behave_data_short %>%
  filter(sub %in% ofc_subs) %>%
  filter(!is.na(RT)) %>%
  filter(trial_type == "Disadvantageous") %>%
  select(sub, chose_equality, round) %>%
  distinct() %>%
  group_by(sub) %>%
  mutate(ten_ten = if_else(chose_equality == "10-10", 1, 0)) %>%
  mutate(ten_count_sub = sum(ten_ten)) %>%
  mutate(num_choices = n()) %>%
  mutate(ten_prob_sub = ten_count_sub/num_choices) %>%
  ungroup() %>%
  mutate(ten_prob_full = mean(ten_prob_sub)) %>%
  mutate(ten_prob_sd = sd(ten_prob_sub)) %>%
  mutate(ten_prob_max =  max(ten_prob_sub)) %>%
  mutate(ten_prob_min = min(ten_prob_sub))


# get % time chose equitable on dis trials only #
adv_choice <- behave_data_short %>%
  filter(sub %in% ofc_subs) %>%
  filter(!is.na(RT)) %>%
  filter(trial_type == "Advantageous") %>%
  select(sub, chose_equality, round) %>%
  distinct() %>%
  group_by(sub) %>%
  mutate(ten_ten = if_else(chose_equality == "10-10", 1, 0)) %>%
  mutate(ten_count_sub = sum(ten_ten)) %>%
  mutate(num_choices = n()) %>%
  mutate(ten_prob_sub = ten_count_sub/num_choices) %>%
  ungroup() %>%
  mutate(ten_prob_full = mean(ten_prob_sub)) %>%
  mutate(ten_prob_sd = sd(ten_prob_sub)) %>%
  mutate(ten_prob_max =  max(ten_prob_sub)) %>%
  mutate(ten_prob_min = min(ten_prob_sub))



adv_df <- behavioral_paper_plots_no_equ_df %>% filter(trial_type == "Advantageous")
dis_df <- behavioral_paper_plots_no_equ_df %>% filter(trial_type == "Disadvantageous")

table(adv_df$ten_ten, adv_df$sub)
table(dis_df$ten_ten, dis_df$sub)

```

```{r offer-ranges}

## Overall ##
print(paste0("Range Self Offer: ", range(behave_correl_data$`Self Offer`)[1], ", ", 
             range(behave_correl_data$`Self Offer`)[2]))
print(paste0("Range Other Offer: ", range(behave_correl_data$`Other Offer`)[1], ", ", 
             range(behave_correl_data$`Other Offer`)[2]))

print(paste0("Mean Self Offer: ", mean(behave_correl_data$`Self Offer`)))
print(paste0("SD Self Offer: ", sd(behave_correl_data$`Self Offer`)))

print(paste0("Mean Other Offer: ", mean(behave_correl_data$`Other Offer`)))
print(paste0("SD Other Offer: ", sd(behave_correl_data$`Other Offer`)))

# Adv Only 
adv_only <- behave_correl_data %>% 
  mutate(trial_type = if_else(`Self Offer` == `Other Offer`, "equality",
                                if_else(`Self Offer` > `Other Offer`,
                                        "Advantageous", "Disadvantageous"))) %>%
  filter(trial_type == "Advantageous")

print(paste0("Adv: Range Self Offer: ", range(adv_only$`Self Offer`)[1], ", ", 
             range(adv_only$`Self Offer`)[2]))
print(paste0("Adv: Range Other Offer: ", range(adv_only$`Other Offer`)[1], ", ", 
             range(adv_only$`Other Offer`)[2]))

print(paste0("Adv: Mean Self Offer: ", mean(adv_only$`Self Offer`)))
print(paste0("Adv: SD Self Offer: ", sd(adv_only$`Self Offer`)))

print(paste0("Adv: Mean Other Offer: ", mean(adv_only$`Other Offer`)))
print(paste0("Adv: SD Other Offer: ", sd(adv_only$`Other Offer`)))


# Dis Only 
dis_only <- behave_correl_data %>% 
  mutate(trial_type = if_else(`Self Offer` == `Other Offer`, "equality",
                                if_else(`Self Offer` > `Other Offer`,
                                        "Advantageous", "Disadvantageous"))) %>%
  filter(trial_type == "Disadvantageous")

print(paste0("Dis: Range Self Offer: ", range(dis_only$`Self Offer`)[1], ", ", 
             range(dis_only$`Self Offer`)[2]))
print(paste0("Dis: Range Other Offer: ", range(dis_only$`Other Offer`)[1], ", ", 
             range(dis_only$`Other Offer`)[2]))

print(paste0("Dis: Mean Self Offer: ", mean(dis_only$`Self Offer`)))
print(paste0("Dis: SD Self Offer: ", sd(dis_only$`Self Offer`)))

print(paste0("Dis: Mean Other Offer: ", mean(dis_only$`Other Offer`)))
print(paste0("Dis: SD Other Offer: ", sd(dis_only$`Other Offer`)))


```


## Choice Behavior Analyses

To examine the effect of inequity on choice behavior, we used a logistic linear mixed-effect model with fixed effects of Inequity Type (advantageous vs. disadvantageous), Unsigned Inequity (the absolute difference between one’s offer and the other player’s offer within the inequitable option), their interaction, as well as Self Offer (the amount offered for themselves in the inequitable option) as a controlling factor, and a random effect of patient.

```{r prep-dfs-for-choice-model}

# only use OFC subjects #
ofc_subs <- c("IR9", "IR16",  "IR26", "IR28", "IR35", "IR57", "IR39", "GP51", "DA9", "ST40")

# prep df #
behavioral_paper_plots_df <- behave_data_short %>%
  filter(sub %in% ofc_subs) %>%
  filter(!is.na(ineq_var)) %>%
  select(ineq_var, sub, chose_equality, round, trial_type, self_var_payoff, ineq_var_abs) %>%
  distinct() %>%
  group_by(ineq_var, sub) %>%
  mutate(ten_ten = if_else(chose_equality == "10-10", 1, 0)) %>%
  mutate(ten_count_sub = sum(ten_ten)) %>%
  mutate(num_choices = n()) %>%
  mutate(ten_prob_sub = ten_count_sub/num_choices) %>%
  group_by(ineq_var) %>%
  mutate(ten_prob_full = mean(ten_prob_sub)) %>%
  mutate(ten_prob_max = ten_prob_full + sd(ten_prob_sub)/sqrt(n())) %>%
  mutate(ten_prob_min = ten_prob_full - sd(ten_prob_sub)/sqrt(n()))


behavioral_paper_plots_no_equ_df <- behave_data_short %>%
  filter(trial_type != "equality") %>%
  filter(sub %in% ofc_subs) %>%
  filter(!is.na(ineq_var)) %>%
  select(ineq_var, sub, chose_equality, round, trial_type, self_var_payoff, ineq_var_abs) %>%
  distinct() %>%
  group_by(ineq_var, sub) %>%
  mutate(ten_ten = if_else(chose_equality == "10-10", 1, 0)) %>%
  mutate(ten_count_sub = sum(ten_ten)) %>%
  mutate(num_choices = n()) %>%
  mutate(ten_prob_sub = ten_count_sub/num_choices) %>%
  group_by(ineq_var) %>%
  mutate(ten_prob_full = mean(ten_prob_sub)) %>%
  mutate(ten_prob_max = ten_prob_full + sd(ten_prob_sub)/sqrt(n())) %>%
  mutate(ten_prob_min = ten_prob_full - sd(ten_prob_sub)/sqrt(n())) 

behavioral_paper_plots_no_equ_df_pretty <- behavioral_paper_plots_no_equ_df %>%
  rename("Self-Offer" = self_var_payoff, "Inequity Type" = trial_type,
         "Unsigned Inequity" = ineq_var_abs, "Chose Equitable Option" = ten_ten, "subject" = sub)
```

### Create Choice Interaction Tables

```{r interaction-choice-model}
library(sjPlot)

log_self_ttype_inter1_model <- glmer(`Chose Equitable Option` ~ `Self-Offer` + `Inequity Type` + `Unsigned Inequity` +
                                       `Inequity Type`*`Unsigned Inequity` +  (1|subject), 
                         data = behavioral_paper_plots_no_equ_df_pretty,
                         family = binomial)

summary(log_self_ttype_inter1_model)

tab_model(log_self_ttype_inter1_model)

```

```{r adv-interaction-choice-model}

behavioral_paper_plots_no_equ_df_adv <- behavioral_paper_plots_no_equ_df_pretty %>%
  filter(`Inequity Type` == "Advantageous")

log_self_ttype_inter1_model_adv <- glmer(`Chose Equitable Option` ~ `Self-Offer` +
                                       `Unsigned Inequity`  +  (1|subject), 
                         data = behavioral_paper_plots_no_equ_df_adv,
                         family = binomial)



tab_model(log_self_ttype_inter1_model_adv)

```

```{r dis-interaction-choice-model}


behavioral_paper_plots_no_equ_df_dis <- behavioral_paper_plots_no_equ_df_pretty %>%
  filter(`Inequity Type` == "Disadvantageous")

log_self_ttype_inter1_model_dis <- glmer(`Chose Equitable Option` ~ `Self-Offer` +
                                       `Unsigned Inequity`  +  (1|subject), 
                         data = behavioral_paper_plots_no_equ_df_dis,
                         family = binomial)




tab_model(log_self_ttype_inter1_model_dis)

```

### Figure 1C

```{r hist-choice-plot, warning = F}

# Figure 1C


resubmission_choice_plot <- behavioral_paper_plots_no_equ_df %>%
  ungroup() %>%
  mutate(ineq_var_abs = if_else(ineq_var_abs <= 4, '0-4', if_else(ineq_var_abs <= 8, '4-8', 
                                                                 if_else(ineq_var_abs <= 12, '8-12', 
                                                                         if_else(ineq_var_abs <= 16, '12-16',
                                                                                 if_else(ineq_var_abs <= 20 , '16-20',
                                                                                         '20+')))))) %>%
  mutate(ineq_var_abs = factor(ineq_var_abs, levels = c("0-4", "4-8", "8-12", "12-16", "16-20", "20+"))) %>%
  group_by(trial_type, ineq_var_abs) %>%
  mutate(total_choice = n()) %>%
  add_tally(ten_ten) %>%
  group_by(trial_type, ineq_var_abs, sub) %>%
  mutate(sub_total_choice = n()) %>%
  add_tally(ten_ten, name = "sub_n") %>%
  select(trial_type, ineq_var_abs, n, sub_n, total_choice, sub, sub_total_choice) %>%
  distinct() %>%
  mutate(percent_choice = n/total_choice) %>%
  mutate(sub_percent_choice = sub_n/sub_total_choice) %>%
  mutate(sub_trial_type = paste0(sub, "_", trial_type)) %>%
  ggplot(., aes(x = ineq_var_abs, y = percent_choice, fill = trial_type)) +
  geom_col(position = position_dodge())  +
  geom_point(aes(y = sub_percent_choice, color = trial_type),
          position = position_jitterdodge(jitter.width =.3, dodge.width = 1), color = 'black', alpha = .5)  +
  labs(y = "Probability of selecting the equitable option", 
       x = "Unsigned Inequity", fill = "Inequity Type",
       title = "Subject Choice By Inequity Type and Amount") +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "top",
        axis.title = element_text(family = "Arial", color = '#2D2327', size = 18), 
        axis.text = element_text(family = "Arial", color = '#2D2327', size = 16),
        legend.text = element_text(family = "Arial", color = '#2D2327', size = 16),
        plot.subtitle =  element_text(family = "Arial", color = '#2D2327', size = 16, face = "italic"),
        legend.title  = element_text(family = "Arial", color = '#2D2327', size = 18),
        strip.text  = element_text(family = "Arial", color = '#2D2327', size = 18, face = "bold"),
        plot.title = element_text(family = "Arial", color = '#2D2327', size = 19)) +
  scale_y_continuous(labels = c("0%", "25%", "50%", "75%", "100%"), 
                     breaks = c(0, .25, .5, .75, 1), limits = c(0, 1))


ggsave(filename = path(here(), "figures", "paper", "figure1c_choice_inequity.tif"),
     device = "tiff",
     width = 7.25,
     height = 8.25,
     units = "in",
     dpi = 350,
     plot =   plot(resubmission_choice_plot))

```



## Reaction Time analyses

To examine the effect of inequity on patients’ reaction times, we ran a similar multiple linear mixed-effects regression on the log-scaled reaction times 

```{r rt-model}

# set up #
ofc_subs <- c("IR9", "IR16","IR26", "IR28", "IR35", "IR57", "IR39", "GP51", "DA9", "ST40")
ggthemr("solarized")

# prep df #
behavioral_paper_rt_plots_df <- behave_data_short %>%
  filter(sub %in% ofc_subs) %>%
  filter(!is.na(RT)) %>%
  filter(RT < 5) %>% # timeout after 5
  filter(trial_type != "equality") 


# run model #
maineffect_rt_model <- lmer(log(RT) ~ trial_type + ineq_var_abs  + (1|sub), 
                             data = behavioral_paper_rt_plots_df)

interact_rt_model <- lmerTest::lmer(log(RT) ~ trial_type + ineq_var_abs +  trial_type*ineq_var_abs + (1|sub), 
                             data = behavioral_paper_rt_plots_df)

interact_self_rt_model <- lmerTest::lmer(log(RT) ~ self_var_payoff + trial_type + ineq_var_abs +  trial_type*ineq_var_abs + (1|sub), 
                             data = behavioral_paper_rt_plots_df)

interact_self_inter_rt_model <- lmerTest::lmer(log(RT) ~ self_var_payoff + trial_type + ineq_var_abs + 
                                                 trial_type*ineq_var_abs + self_var_payoff*trial_type + (1|sub), 
                             data = behavioral_paper_rt_plots_df)


summary(interact_rt_model)
summary(interact_self_rt_model)
summary(interact_self_inter_rt_model)

```

### RT Interaction Tables

```{r pretty-rt-model-table}

behavioral_paper_rt_plots_df_pretty <- behave_data_short %>%
  filter(sub %in% ofc_subs) %>%
  filter(!is.na(RT)) %>%
  filter(RT < 5) %>% # timeout after 5
  filter(trial_type != "equality") %>%
  mutate(RT = log(RT)) %>%
  rename("Self-Offer" = self_var_payoff, "Inequity Type" = trial_type,
         "Unsigned Inequity" = ineq_var_abs, "Reaction Time (log-scaled)" = RT, "subject" = sub)


interact_self_rt_model <- lmerTest::lmer(`Reaction Time (log-scaled)` ~ 
                                           `Self-Offer` + `Inequity Type` + `Unsigned Inequity` +  
                                           `Inequity Type`*`Unsigned Inequity` + (1|subject), 
                             data = behavioral_paper_rt_plots_df_pretty)

tab_model(interact_self_rt_model)


```

```{r adv-only-rt-model}

adv_behavioral_paper_rt_plots_df_pretty <- behavioral_paper_rt_plots_df_pretty %>%
  filter(`Inequity Type` == "Advantageous")


adv_interact_self_rt_model <- lmerTest::lmer(`Reaction Time (log-scaled)` ~ 
                                           `Self-Offer` + `Unsigned Inequity`  + (1|subject), 
                             data = adv_behavioral_paper_rt_plots_df_pretty)

tab_model(adv_interact_self_rt_model)


```

```{r dis-only-rt-model}

dis_behavioral_paper_rt_plots_df_pretty <- behavioral_paper_rt_plots_df_pretty %>%
  filter(`Inequity Type` == "Disadvantageous")


dis_interact_self_rt_model <- lmerTest::lmer(`Reaction Time (log-scaled)` ~ 
                                           `Self-Offer` + `Unsigned Inequity`  + (1|subject), 
                             data = dis_behavioral_paper_rt_plots_df_pretty)

tab_model(dis_interact_self_rt_model)


```

### Figure 1D

```{r rt-plot-for-resubmission}

# Code for Figure 1D #

resubmission_rt_plot <- behavioral_paper_rt_plots_df %>%
  ungroup() %>%
  group_by(ineq_var, sub) %>%
  mutate(sub_mean_rt = mean(RT)) %>%
  select(sub, sub_mean_rt, ineq_var, trial_type, ineq_var_abs) %>%
  distinct() %>%
  group_by(ineq_var) %>%
  mutate(mean_rt = mean(sub_mean_rt)) %>%
  ggplot(., aes(x = factor(ineq_var_abs), y = mean_rt, fill = trial_type)) +
  geom_col(position = position_dodge()) +
  geom_point(aes(y = sub_mean_rt, color = trial_type),position = position_dodge(width = 1), color = "black", alpha = .5) +
  geom_line(aes(group = sub, y = sub_mean_rt), color = "black", alpha = .5) +
  labs(y = "RT (in seconds)", 
       x = "Unsigned Inequity", fill = "Inequity Type",
       title = "Average Reaction Times by Inequity Type and Amount", subtitle = "Faster RTs are associated with higher inequity in Adv. but not Dis. trials") +
  theme(panel.background = element_rect(fill = "white"), 
        legend.position = "none",
        axis.title = element_text(family = "Arial", color = '#2D2327', size = 18), 
        axis.text = element_text(family = "Arial", color = '#2D2327', size = 16),
        legend.text = element_text(family = "Arial", color = '#2D2327', size = 16),
        plot.subtitle =  element_text(family = "Arial", color = '#2D2327', size = 16, face = "italic"),
        legend.title  = element_text(family = "Arial", color = '#2D2327', size = 18),
        strip.text  = element_text(family = "Arial", color = '#2D2327', size = 18, face = "bold"),
        plot.title = element_text(family = "Arial", color = '#2D2327', size = 20)) +
  facet_wrap(~trial_type, scales = "free_x")


ggsave(filename = path(here(), "figures", "paper", "figure1d_rt_correlations.tif"),
     device = "tiff",
     width = 9.5,
     height = 8.5,
     units = "in",
     dpi = 350,
     plot =   plot(resubmission_rt_plot))


```



```{r correlations-for-indv-subs}

# Individualized correlations of the RT effect, Supplemental Figure 2 #

adv_individual_correl_plot <- behavioral_paper_rt_plots_df %>%
  filter(trial_type == "Advantageous") %>%
  ggplot(., aes(y = log(RT), x = ineq_var_abs)) + 
  geom_jitter(fill = "grey", width = .5) +
  geom_smooth(method = "lm", formula = "y ~ x", color = "black", fill = "grey") +
  labs(y = "Log-scaled Reaction Time", 
       x = "",
       subtitle = "Individual Subject Correlations in Advantageous Trials Only",
       title = "Effects of Inequity Type and Absolute Inequity on Reaction Times", 
       color = "Inequity Type") +
  theme(panel.background = element_rect(fill = "white"), 
        legend.position = "top",
        axis.title = element_text(family = "Arial", color = '#2D2327', size = 14), 
        strip.text = element_text(family = "Arial", color = '#2D2327', size = 12, face = 'bold'), 
        axis.text = element_text(family = "Arial", color = '#2D2327', size = 12),
        legend.text = element_text(family = "Arial", color = '#2D2327', size = 12),
        plot.subtitle =  element_text(family = "Arial", color = '#2D2327', size = 12, face = "italic"),
        legend.title  = element_text(family = "Arial", color = '#2D2327', size = 14),
        plot.title = element_text(family = "Arial", color = '#2D2327', size = 15)) +
  scale_color_manual(values = c("#5BA6D6")) +
  scale_fill_manual(values = c("#5BA6D6"), guide = "none") +
  scale_y_continuous(limits = c(-1.2, 1.6), breaks = c(-.9, 0, .9)) +
  facet_wrap(~sub, nrow = 2)

dis_individual_correl_plot <- behavioral_paper_rt_plots_df %>%
  filter(trial_type == "Disadvantageous") %>%
  ggplot(., aes(y = log(RT), x = ineq_var_abs)) + 
  geom_jitter(fill = "grey", color = "#E4635C", width = .5) +
  geom_smooth(method = "lm", formula = "y ~ x", color = "black", fill = "grey") +
  labs(y = "Log-scaled Reaction Time", 
       x = "         Inequity",
       subtitle = "Individual Subject Correlations in Disadvantageous Trials Only", 
       color = "Inequity Type") +
  theme(panel.background = element_rect(fill = "white"), 
        legend.position = "top",
        axis.title = element_text(family = "Arial", color = '#2D2327', size = 14), 
        strip.text = element_text(family = "Arial", color = '#2D2327', size = 12, face = 'bold'), 
        axis.text = element_text(family = "Arial", color = '#2D2327', size = 12),
        legend.text = element_text(family = "Arial", color = '#2D2327', size = 12),
        plot.subtitle =  element_text(family = "Arial", color = '#2D2327', size = 12, face = "italic"),
        legend.title  = element_text(family = "Arial", color = '#2D2327', size = 14),
        plot.title = element_text(family = "Arial", color = '#2D2327', size = 15)) +
  scale_color_manual(values = c("#E4635C")) +
  scale_fill_manual(values = c("#E4635C"), guide = "none") +
  scale_y_continuous(limits = c(-1.2, 1.6), breaks = c(-.9, 0, .9)) +
  scale_x_continuous(breaks = c(5, 10, 15, 20, 25)) +
  facet_wrap(~sub, nrow = 2)


ggsave(filename = path(here(), "figures", "paper", "individual_rt_correlationss.png"),
     device = "png",
     width = 9,
     height = 12,
     units = "in",
     dpi = 300,
     plot =   arrangeGrob(grobs = list(adv_individual_correl_plot, 
                                       dis_individual_correl_plot), nrow = 2, ncol = 1))

```




