---
title: "Localization Analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 5,  # set default width of figures
  fig.height <- 8,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
# library(summarytools)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(ggalluvial)
library(factoextra)
library(NbClust)
library(lme4)
library(afex)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "compile_mult_reg_results.R"))
source(path(here(), "R", "compile_mult_reg_results.R"))
# source('~/Projects/nice_r_functions/ggpaired_pretty.R')
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "load_and_collate_reg_results.R"))



## plotting helpers ##
ggthemr("solarized")
getPalette = colorRampPalette(brewer.pal(10, "Set2"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 4
# registerDoParallel(nCores)
# 


#find . -type f -mtime +10 -maxdepth 1 -exec mv {} before_3-21-21 \;
```


# Anatomical Analyses

To determine if the effects of our above analyses were localized to a specific region of the OFC we used linear mixed-effects modeling. Specifically, we averaged the MNI coordinates of the bipolar-referenced electrodes for each MNI axis. We then tested if the MNI coordinate predicted the test statistic, using a different model for each MNI axis, each with a random effect of subject. We then tested if the MNI coordinate predicted the test statistic, using a different model for each MNI axis, each with a random effect of subject. See the above methods for the definition of the test statistic. We ran these analyses for both the unified and state-dependent encoding analyses first grouped across all predictors, and then separately for each of our main predictors (Self-Offer, Other-Offer, Inequity Type).

In order to refine the regional analysis, we also used the human Brainnetome Atlas (Fan et al., 2016). OFC electrodes were classified into 12 subregions: we included all subregions within the Orbital group of the Brainntome atlas, regions in the Superior and Middle Frontal group that included Broadman area 10, as well as subgenual area 32 from the Cingulate group. Following the approach used by Golan et al. (2016), for each one of our variable of interest (Self-Offer, Other-Offer and Inequity Type in the Unified analyses, and Self-Offer and Other-Offer in the Split analyses), we fitted the log transform of the variable’s test statistic with a one-way mixed-effects model with the fixed factor of Brainnetome region, and the random factors of epoch and patients. Bipolar electrodes were classified according to the Brainnetome location of the first electrode of each pair.

## Load and Prep Data

```{r load-anat-data}
# load main localization file #
localizations <- read_csv(path(here(), "munge", "combined_electrode_info_with_bob.csv"))

# load ST40 file with added Braintomme regions #
st40_localizations <- read_csv(path(here(), "electrode_coverage", "ST40_Elec_Notes_wAtlases.csv"))
st40_localizations <- st40_localizations %>%
  mutate(subject = "ST40") %>%
  rename(Coordinates = `Coordinates [MNI]`) %>%
  select(subject, Electrode, Brainnetome, Coordinates) 

# prep correct st40 df #
st40_orig_localizations <- localizations %>%
  filter(subject == "ST40") %>%
  select(-Brainnetome, -Coordinates)

st40_localizations <- left_join(st40_orig_localizations, st40_localizations)

# merge st40 back with other subjects #
localizations <- localizations %>%
  filter(subject != "ST40")

localizations_clean <- full_join(localizations, st40_localizations)

# clean braintome names
localizations_clean <- localizations_clean %>%
  mutate(Brainnetome = gsub(";", ",", Brainnetome)) %>%
  mutate(Brainnetome = if_else(Brainnetome == "no_label_found", "no_label_found",
                              sub(".*?, ", "", gsub(" \\(.*", "", Brainnetome))))

# clean df and prep for merging
braintome_clean <- localizations_clean %>%
  select(subject, Electrode, Brainnetome, Coordinates) %>%
  mutate(Electrode = gsub("POL ", "", Electrode)) %>%
  mutate(Electrode = gsub(" POL", "", Electrode)) %>%
  mutate(Electrode = gsub("-Ref", "", Electrode)) %>%
  mutate(Electrode = gsub("-Ref-", "-", Electrode)) %>%
  mutate(first_elec = Electrode) %>%
  mutate(second_elec = Electrode) %>%
  mutate(first_elec_braint = Brainnetome) %>%
  mutate(second_elec_braint = Brainnetome) %>%  
  mutate(first_mni_coord = Coordinates) %>%
  mutate(second_mni_coord = Coordinates) %>%  
  select(-Electrode, -Brainnetome, -Coordinates) 

```


```{r load-data-unified-and-split-data}

## unified data ##
unified_hfa_data <- read_csv(path(here(), "results", "single_regressions",
                                  "compiled_unified_ogpermutation_ofc_results_1_26_2022_anatomy.csv"))

# predictors of interest
unified_hfa_data <- unified_hfa_data %>% filter(predictor %in% c("self_var_payoff", "other_var_payoff", "trial_type"))

unified_braintome_data <- left_join(unified_hfa_data, braintome_clean %>% select(-second_elec, -second_elec_braint, -second_mni_coord))
unified_braintome_data <- left_join(unified_braintome_data, braintome_clean %>% select(-first_elec, -first_elec_braint, -first_mni_coord))

# fix coordinates for ST40 from old incorrect recon
unified_braintome_data <- unified_braintome_data %>%
  separate(first_mni_coord, into = c("first_mni_x", "first_mni_y", "first_mni_z"), sep = "    ") %>%
  separate(second_mni_coord, into = c("second_mni_x", "second_mni_y", "second_mni_z"), sep = "    ") %>%
  mutate_at(.vars = vars("first_mni_x", "first_mni_y", "first_mni_z", 
                         "second_mni_x", "second_mni_y", "second_mni_z"), .funs = function(x) as.numeric(x)) %>%
  select(-first_elec_x, -first_elec_y, -first_elec_z)

braintome_elec_id_data <- unified_braintome_data %>%
  select(subject, electrode, starts_with("first_"), starts_with("second") ) %>%
  distinct() 



## split data ##
# load permuted regressor results #
split_ofc_encoding_reg_df <- read_csv(path(here(), "results", "single_regressions",
                                       "compiled_ofc_ogpermutation_wpvalues_single_regressions_1_28_2022.csv"))

# load permuted trial results #
split_ofc_encoding_ttype_df <- read_csv(path(here(), "results", "single_regressions",
                                       "compiled_ofc_ogpermutation_ttype_wpvalues_single_regressions_1_28_2022.csv"))

# rename test stats and combine #
split_ofc_encoding_reg_df <- split_ofc_encoding_reg_df %>%
  rename(test_stat_real_reg = test_stat_real) %>%
  rename(permuted_p_reg = permuted_p)

split_ofc_encoding_ttype_df <- split_ofc_encoding_ttype_df %>%
  rename(test_stat_real_ttype = test_stat_real) %>%
  rename(permuted_p_ttype = permuted_p)

split_ofc_encoding_df <- full_join(split_ofc_encoding_reg_df, split_ofc_encoding_ttype_df)

## bind split data iwth braintome data ##
split_braintome_data <- left_join(split_ofc_encoding_df, braintome_elec_id_data)

```


```{r identify-bad-lables}


# ALl ST40 electrodes are on the left except for OF5, OF6
braintome_bad_rois <- braintome_elec_id_data %>%
  filter(first_elec_braint %in% c("Left Basal Ganglia dCa, dorsal caudate", "Left Basal Ganglia vCa, ventral caudate",
                                  "no_label_found", "Right Insular Gyrus dIa, dorsal agranular insula"))

# other not orbinal
not_orb_only <- unified_braintome_data %>%
  select(subject, electrode, starts_with("first"), starts_with("second")) %>%
  distinct() %>%
  filter(!grepl("Orb", first_elec_braint))

## Unified ##

# manual updating of brantome regions based on expert consultation with nurologist + braintome atlas
unified_braintome_data <- unified_braintome_data %>%
  mutate(first_elec_braint = if_else(subject == "IR9" & first_elec == "ROF2", "Right Orbital Gyrus A11l, lateral area 11",
         if_else(subject == "IR9" & first_elec == "ROF4", "Right Orbital Gyrus A11l, lateral area 11",
          if_else(subject == "IR9" & first_elec == "ROF5", "no_label_found",
            if_else(subject == "IR9" & first_elec == "ROF6", "Right Orbital Gyrus A12/47l, lateral area 12/47",
              if_else(subject == "IR9" & first_elec == "ROF7", "Right Orbital Gyrus A12/47l, lateral area 12/47",
            if_else(subject == "ST40" & first_elec == "MVF4", "Left Cingulate Gyrus A32sg, subgenual area 32", 
                if_else(subject == "ST40" & first_elec == "OF1", "Left Orbital Gyrus A11l, lateral area 11", 
                    if_else(subject == "ST40" & first_elec == "PVF1", "Left Orbital Gyrus A13, area 13",
                      if_else(subject == "ST40" & first_elec == "PVF2", "Left Orbital Gyrus A13, area 13",
                        if_else(subject == "ST40" & first_elec == "PVF3", "Left Cingulate Gyrus A32sg, subgenual area 32",
                          if_else(subject == "ST40" & first_elec == "PVF4", "Left Cingulate Gyrus A32sg, subgenual area 32",
                              if_else(subject == "IR26" & first_elec == "ROF3", "Right Middle Frontal Gyrus A10l, lateral area10",
                                  first_elec_braint))))))))))))) %>%
  mutate(second_elec_braint = if_else(subject == "IR9" & second_elec == "ROF2", "Right Orbital Gyrus A11l, lateral area 11",
         if_else(subject == "IR9" & second_elec == "ROF4", "Right Orbital Gyrus A11l, lateral area 11",
           if_else(subject == "IR9" & first_elec == "ROF5", "no_label_found",
            if_else(subject == "IR9" & first_elec == "ROF6", "Right Orbital Gyrus A12/47l, lateral area 12/47",
              if_else(subject == "IR9" & first_elec == "ROF7", "Right Orbital Gyrus A12/47l, lateral area 12/47",
            if_else(subject == "ST40" & second_elec == "MVF4", "Left Cingulate Gyrus A32sg, subgenual area 32", 
                if_else(subject == "ST40" & second_elec == "OF1", "Left Orbital Gyrus A11l, lateral area 11", 
                    if_else(subject == "ST40" & second_elec == "PVF1", "Left Orbital Gyrus A13, area 13",
                      if_else(subject == "ST40" & second_elec == "PVF2", "Left Orbital Gyrus A13, area 13",
                        if_else(subject == "ST40" & second_elec == "PVF3", "Left Cingulate Gyrus A32sg, subgenual area 32",
                          if_else(subject == "ST40" & second_elec == "PVF4", "Left Cingulate Gyrus A32sg, subgenual area 32",
                              if_else(subject == "IR26" & first_elec == "ROF3", "Right Middle Frontal Gyrus A10l, lateral area10",
                                  second_elec_braint)))))))))))))  %>%
  # if the 'first_elec_braint' == "no_label_found" it isn't an OFC electrode, after addressing the above exceptions. All other first elecs are OFC
  mutate(first_elec_braint = replace(first_elec_braint, first_elec_braint == "no_label_found", NA)) %>%
  mutate(second_elec_braint = replace(second_elec_braint, second_elec_braint == "no_label_found", NA)) %>%
  # there are no new second electrodes that aren't also first electrodes in the OFC, so the list of the first is the list of OFC regions
  mutate(second_elec_braint = replace(second_elec_braint, !(second_elec_braint %in% unique(first_elec_braint)), NA))
  
# should all be true
table(unique(unified_braintome_data$second_elec_braint) %in% unique(unified_braintome_data$first_elec_braint))


## SPLIT ##

# manual updating of brantome regions based on expert consultation with nurologist + braintome atlas
split_braintome_data <- split_braintome_data %>%
  mutate(first_elec_braint = if_else(subject == "IR9" & first_elec == "ROF2", "Right Orbital Gyrus A11l, lateral area 11",
         if_else(subject == "IR9" & first_elec == "ROF4", "Right Orbital Gyrus A11l, lateral area 11",
          if_else(subject == "IR9" & first_elec == "ROF5", "no_label_found",
            if_else(subject == "IR9" & first_elec == "ROF6", "Right Orbital Gyrus A12/47l, lateral area 12/47",
              if_else(subject == "IR9" & first_elec == "ROF7", "Right Orbital Gyrus A12/47l, lateral area 12/47",
            if_else(subject == "ST40" & first_elec == "MVF4", "Left Cingulate Gyrus A32sg, subgenual area 32", 
                if_else(subject == "ST40" & first_elec == "OF1", "Left Orbital Gyrus A11l, lateral area 11", 
                    if_else(subject == "ST40" & first_elec == "PVF1", "Left Orbital Gyrus A13, area 13",
                      if_else(subject == "ST40" & first_elec == "PVF2", "Left Orbital Gyrus A13, area 13",
                        if_else(subject == "ST40" & first_elec == "PVF3", "Left Cingulate Gyrus A32sg, subgenual area 32",
                          if_else(subject == "ST40" & first_elec == "PVF4", "Left Cingulate Gyrus A32sg, subgenual area 32",
                              if_else(subject == "IR26" & first_elec == "ROF3", "Right Middle Frontal Gyrus A10l, lateral area10",
                                  first_elec_braint))))))))))))) %>%
  mutate(second_elec_braint = if_else(subject == "IR9" & second_elec == "ROF2", "Right Orbital Gyrus A11l, lateral area 11",
         if_else(subject == "IR9" & second_elec == "ROF4", "Right Orbital Gyrus A11l, lateral area 11",
           if_else(subject == "IR9" & first_elec == "ROF5", "no_label_found",
            if_else(subject == "IR9" & first_elec == "ROF6", "Right Orbital Gyrus A12/47l, lateral area 12/47",
              if_else(subject == "IR9" & first_elec == "ROF7", "Right Orbital Gyrus A12/47l, lateral area 12/47",
            if_else(subject == "ST40" & second_elec == "MVF4", "Left Cingulate Gyrus A32sg, subgenual area 32", 
                if_else(subject == "ST40" & second_elec == "OF1", "Left Orbital Gyrus A11l, lateral area 11", 
                    if_else(subject == "ST40" & second_elec == "PVF1", "Left Orbital Gyrus A13, area 13",
                      if_else(subject == "ST40" & second_elec == "PVF2", "Left Orbital Gyrus A13, area 13",
                        if_else(subject == "ST40" & second_elec == "PVF3", "Left Cingulate Gyrus A32sg, subgenual area 32",
                          if_else(subject == "ST40" & second_elec == "PVF4", "Left Cingulate Gyrus A32sg, subgenual area 32",
                              if_else(subject == "IR26" & first_elec == "ROF3", "Right Middle Frontal Gyrus A10l, lateral area10",
                                  second_elec_braint)))))))))))))  %>%
  # if the 'first_elec_braint' == "no_label_found" it isn't an OFC electrode, after addressing the above exceptions. All other first elecs are OFC
  mutate(first_elec_braint = replace(first_elec_braint, first_elec_braint == "no_label_found", NA)) %>%
  mutate(second_elec_braint = replace(second_elec_braint, second_elec_braint == "no_label_found", NA)) %>%
  # there are no new second electrodes that aren't also first electrodes in the OFC, so the list of the first is the list of OFC regions
  mutate(second_elec_braint = replace(second_elec_braint, !(second_elec_braint %in% unique(first_elec_braint)), NA))
  
# should all be true
table(unique(split_braintome_data$second_elec_braint) %in% unique(split_braintome_data$first_elec_braint))

```


```{r alternate-hyp-removal}

## electrodes with differences in noise between trial types ##
trial_dep_noise_df <- read_csv(path(here(), "results", "trial_dep_differences_noise.csv"))


## electrodes better explained by max/min unified encoding ##
split_v_uni_max_df <- read_csv(path(here(), "results", "unified_max_split_elecs.csv"))

```

```{r prep-dfs}

## remove noisy, possible unified electrodes ##
split_braintome_data <- split_braintome_data %>%
  mutate(elec_epoch_ids = paste(subject, electrode, epoch, sep = "_")) %>%
  filter(!elec_epoch_ids %in% trial_dep_noise_df$elec_epoch_ids) %>%
  filter(!reg_id %in% split_v_uni_max_df$reg_id)


## split ##
split_braintome_data_clean <- split_braintome_data %>%
  # remove duplicate test statistic
  rename(test_stat_real = test_stat_real_reg) %>%
  select(reg_id, subject, electrode, predictor, epoch, test_stat_real, starts_with("first_"), starts_with("second_")) %>%
  distinct() %>%
  rowwise() %>%
  mutate(average_x = mean(first_mni_x, second_mni_x)) %>%
  mutate(average_y = mean(first_mni_y, second_mni_y)) %>%
  mutate(average_z = mean(first_mni_z, second_mni_z)) %>%
  ungroup()

# unified #
unified_braintome_data_clean <- unified_braintome_data %>%
  mutate(elec_id = paste(subject, electrode, sep = "_")) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  select(reg_id, subject, electrode, predictor, epoch, perm_p, fstretch, bstretch, starts_with("first_"), starts_with("second_")) %>%
  distinct() %>%
  rowwise() %>%
  mutate(average_x = mean(first_mni_x, second_mni_x)) %>%
  mutate(average_y = mean(first_mni_y, second_mni_y)) %>%
  mutate(average_z = mean(first_mni_z, second_mni_z)) %>%
  ungroup()

# combine across hemispheres #
noHem_unified_braintome_data_clean <- unified_braintome_data_clean %>%
  mutate(first_elec_braint = gsub("Left ", "", first_elec_braint)) %>%
  mutate(first_elec_braint = gsub("Right ", "", first_elec_braint)) %>%
  mutate(second_elec_braint = gsub("Left ", "", second_elec_braint)) %>%
  mutate(second_elec_braint = gsub("Right ", "", second_elec_braint)) 

noHem_split_braintome_data_clean <- split_braintome_data_clean %>%
  mutate(first_elec_braint = gsub("Left ", "", first_elec_braint)) %>%
  mutate(first_elec_braint = gsub("Right ", "", first_elec_braint)) %>%
  mutate(second_elec_braint = gsub("Left ", "", second_elec_braint)) %>%
  mutate(second_elec_braint = gsub("Right ", "", second_elec_braint)) 

```

```{r get-bilat-unilat-nums}

laterality_df <- unified_braintome_data_clean %>%
  ungroup() %>%
  select(subject, first_elec, first_elec_braint, second_elec, second_elec_braint) %>%
  distinct() %>%
  mutate(lat = if_else(grepl("^Left", first_elec_braint), "Left",
                      if_else(grepl("^Right", first_elec_braint), "Right", "check"))) %>%
  filter(lat != "check") %>%
  select(subject, lat) %>%
  distinct()


```

```{r print-regions}

unique(c(noHem_unified_braintome_data_clean$first_elec_braint, noHem_unified_braintome_data_clean$second_elec_braint))

```


# Braintome Regression Analysis

## Unified


```{r unified-afex}


unified_model_ttype <- mixed(log(fstretch) ~ first_elec_braint  + (1|subject)+  (1|epoch), 
                                               data = noHem_unified_braintome_data_clean %>% filter(predictor == "trial_type"))
unified_model_ttype

unified_model_self <- mixed(log(fstretch) ~ first_elec_braint  +  (1|subject) +  (1|epoch), 
                                              data = noHem_unified_braintome_data_clean %>% filter(predictor == "self_var_payoff"))
unified_model_self

unified_model_other <- mixed(log(fstretch) ~ first_elec_braint +  (1|subject) +  (1|epoch), 
                                               data = noHem_unified_braintome_data_clean %>% filter(predictor == "other_var_payoff"))
unified_model_other


```


## Split


```{r split-brainntome-afex}


split_model_self <- mixed(log(test_stat_real) ~ first_elec_braint  +  (1|subject) +  (1|epoch), 
                                              data = noHem_split_braintome_data_clean %>% filter(predictor == "self_var_payoff"))
split_model_self

split_model_other <- mixed(log(test_stat_real) ~ first_elec_braint  + (1|subject) +  (1|epoch), 
                                               data = noHem_split_braintome_data_clean %>% filter(predictor == "other_var_payoff"))
split_model_other


```




# Gradient Analyses

##  Unified 

```{r unified-localization-ttype}

# overall #
ttype_electrode_unified_model_x <- lmer(fstretch ~  + average_x + (1|subject)  +  (1|epoch), data = noHem_unified_braintome_data_clean %>% filter(predictor == 'trial_type'))
ttype_electrode_unified_model_y <- lmer(fstretch ~ average_y +  (1|subject) +  (1|epoch), data = noHem_unified_braintome_data_clean %>% filter(predictor == 'trial_type'))
ttype_electrode_unified_model_z <- lmer(fstretch ~ average_z +  (1|subject)  +  (1|epoch), data = noHem_unified_braintome_data_clean %>% filter(predictor == 'trial_type'))
summary(ttype_electrode_unified_model_x)
summary(ttype_electrode_unified_model_y)
summary(ttype_electrode_unified_model_z)
```

```{r unified-localization-otherv}

# overall #
otherv_electrode_unified_model_x <- lmer(log(fstretch) ~ average_x +  (1|subject) +  (1|epoch), data = noHem_unified_braintome_data_clean%>% filter(predictor == 'other_var_payoff'))
otherv_electrode_unified_model_y <- lmer(log(fstretch) ~ average_y +  (1|subject) +  (1|epoch), data = noHem_unified_braintome_data_clean %>% filter(predictor == 'other_var_payoff'))
otherv_electrode_unified_model_z <- lmer(log(fstretch) ~ average_z +  (1|subject) +  (1|epoch), data = noHem_unified_braintome_data_clean %>% filter(predictor == 'other_var_payoff'))
summary(otherv_electrode_unified_model_x)
summary(otherv_electrode_unified_model_y)
summary(otherv_electrode_unified_model_z)

```

```{r unified-localization-selfv}

# overall #
selfv_electrode_unified_model_x <- lmer(log(fstretch) ~ average_x +  (1|subject) +  (1|epoch), data = noHem_unified_braintome_data_clean%>% filter(predictor == 'self_var_payoff'))
selfv_electrode_unified_model_y <- lmer(log(fstretch) ~ average_y +  (1|subject) +  (1|epoch), data = noHem_unified_braintome_data_clean %>% filter(predictor == 'self_var_payoff'))
selfv_electrode_unified_model_z <- lmer(log(fstretch) ~ average_z +  (1|subject) +  (1|epoch), data = noHem_unified_braintome_data_clean %>% filter(predictor == 'self_var_payoff'))
summary(selfv_electrode_unified_model_x)
summary(selfv_electrode_unified_model_y)
summary(selfv_electrode_unified_model_z)

```

## State Dependent Localization Results

```{r split-localization-otherv}

otherv_electrode_split_model_x <- lmer(log(test_stat_real) ~ average_x +  (1|subject) +  (1|epoch), 
                                             data = noHem_split_braintome_data_clean %>% filter(predictor == 'other_var_payoff'))
otherv_electrode_split_model_y <- lmer(log(test_stat_real) ~ average_y +  (1|subject) +  (1|epoch), 
                                             data = noHem_split_braintome_data_clean  %>% filter(predictor == 'other_var_payoff'))
otherv_electrode_split_model_z <- lmer(log(test_stat_real) ~ average_z +  (1|subject) +  (1|epoch), 
                                             data = noHem_split_braintome_data_clean  %>% filter(predictor == 'other_var_payoff'))
summary(otherv_electrode_split_model_x)
summary(otherv_electrode_split_model_y)
summary(otherv_electrode_split_model_z)


```

```{r split-localization-selfv}


selfv_electrode_split_model_x <- lmer(log(test_stat_real) ~ average_x +  (1|subject) +  (1|epoch), data = noHem_split_braintome_data_clean%>% filter(predictor == 'self_var_payoff'))
selfv_electrode_split_model_y <- lmer(log(test_stat_real) ~ average_y +  (1|subject) +  (1|epoch), data = noHem_split_braintome_data_clean %>% filter(predictor == 'self_var_payoff'))
selfv_electrode_split_model_z <- lmer(log(test_stat_real) ~ average_z +  (1|subject) +  (1|epoch), data = noHem_split_braintome_data_clean %>% filter(predictor == 'self_var_payoff'))
summary(selfv_electrode_split_model_x)
summary(selfv_electrode_split_model_y)
summary(selfv_electrode_split_model_z)




```





