---
title: "Noise Comparisons between trial types"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 5,  # set default width of figures
  fig.height <- 8,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
# library(summarytools)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(ggalluvial)
library(parameters)
library(factoextra)
library(NbClust)
library(ggsankey)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "compile_mult_reg_results.R"))
source(path(here(), "R", "compile_mult_reg_results.R"))
# source('~/Projects/nice_r_functions/ggpaired_pretty.R')
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "load_and_collate_reg_results.R"))



## plotting helpers ##
ggthemr("solarized")
getPalette = colorRampPalette(brewer.pal(9, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 4
# registerDoParallel(nCores)
# 


#find . -type f -mtime +10 -maxdepth 1 -exec mv {} before_3-21-21 \;
```

## Alternate Hypothesis: Noise Across Different Trial Types

To test if differences in noise between the two trial types was driving our inequity-dependent encoding results, in this analysis we test for significant differences between the residuals in each epoch for both self offer and other offer. If the confidence interval around the difference in means of the residuals did not include 0, we will exclude that electrode-epoch from the inequity-dependent analyses

```{r load-data}
# load permuted regressor results #
split_ofc_encoding_reg_df <- read_csv(path(here(), "results", "single_regressions",
                                       "compiled_ofc_ogpermutation_wpvalues_single_regressions_1_28_2022.csv"))

# load permuted trial results #
split_ofc_encoding_ttype_df <- read_csv(path(here(), "results", "single_regressions",
                                       "compiled_ofc_ogpermutation_ttype_wpvalues_single_regressions_1_28_2022.csv"))

# rename test stats and combine #
split_ofc_encoding_reg_df <- split_ofc_encoding_reg_df %>%
  rename(test_stat_real_reg = test_stat_real) %>%
  rename(permuted_p_reg = permuted_p)

split_ofc_encoding_ttype_df <- split_ofc_encoding_ttype_df %>%
  rename(test_stat_real_ttype = test_stat_real) %>%
  rename(permuted_p_ttype = permuted_p)

split_ofc_encoding_df <- full_join(split_ofc_encoding_reg_df, split_ofc_encoding_ttype_df)


```

```{r prep-dfs}

# percentage of elecs acros epochs
split_ofc_encoding_reg_sig <- split_ofc_encoding_df %>%
  filter(permuted_p_reg < 0.05) %>%
  select(subject, electrode, predictor, epoch, permuted_p_reg) %>%
  distinct() %>%
  group_by(predictor, epoch) %>%
  mutate(sig_count = n()) %>%
  mutate(percent_of_elecs = (sig_count/ 136) * 100)

split_ofc_encoding_ttype_sig <- split_ofc_encoding_df %>%
  filter(permuted_p_ttype < 0.05) %>%
  select(subject, electrode, predictor, epoch, permuted_p_ttype) %>%
  distinct() %>%
  group_by(predictor, epoch) %>%
  mutate(sig_count = n()) %>%
  mutate(percent_of_elecs = (sig_count/ 136) * 100)


split_ofc_encoding_sig <- split_ofc_encoding_df %>%
  filter(permuted_p_ttype < 0.05 & permuted_p_reg < 0.05) %>%
  select(subject, electrode, predictor, epoch, permuted_p_ttype, permuted_p_reg) %>%
  distinct() %>%
  group_by(predictor, epoch) %>%
  mutate(sig_count = n()) %>%
  mutate(percent_of_elecs = (sig_count/ 136) * 100)


# fdr correctyed df 
split_ofc_encoding_df_fdr <- split_ofc_encoding_df %>%
  select(reg_id, subject, electrode, predictor, epoch, permuted_p_reg, permuted_p_ttype) %>%
  distinct() %>%
  group_by(epoch, predictor) %>%
  mutate(perm_p_reg_fdr = p.adjust(permuted_p_reg, method = "fdr")) %>%
  mutate(perm_p_ttype_fdr = p.adjust(permuted_p_ttype, method = "fdr"))


scatter_plot_r2_df <- split_ofc_encoding_df %>%
  group_by(reg_id) %>%
  mutate(mean_adv = mean(Advantageous)) %>%
  mutate(mean_dis = mean(Disadvantageous)) %>%
  select(mean_adv, mean_dis, reg_id) %>%
  distinct() 

scatter_plot_r2_fdr_df <- left_join(scatter_plot_r2_df, split_ofc_encoding_df_fdr)


scatter_plot_r2_fdr_df <- scatter_plot_r2_fdr_df %>%
  mutate(sig = if_else(mean_dis > mean_adv & perm_p_reg_fdr < 0.05 & perm_p_ttype_fdr < 0.05, "Disadvantageous", 
                       if_else(mean_adv >= mean_dis & perm_p_reg_fdr < 0.05 & perm_p_ttype_fdr < 0.05, "Advantegous", "Not Sig.")))

```


```{r load-raw-hfa-data, echo = F}

# load hfa data #
all_brain_data_pres <-  read_csv(path(here(), "/munge/all_brain_data_pres_1_3_2022.csv"), 
                                 col_types = cols())
all_brain_data_pre_choice <-  read_csv(path(here(), "/munge/all_brain_data_pre_choice_1_3_2022.csv"), 
                                       col_types = cols())
all_brain_data_post_choice <-  read_csv(path(here(), "/munge/all_brain_data_post_choice_1_3_2022.csv"),
                                        col_types = cols())

# make elec id col
all_brain_data_pres <- all_brain_data_pres %>%
  mutate(elec_ids = paste0(subject, "_", electrodes))

all_brain_data_pre_choice <- all_brain_data_pre_choice %>%
  mutate(elec_ids = paste0(subject, "_", electrodes))

all_brain_data_post_choice <- all_brain_data_post_choice %>%
  mutate(elec_ids = paste0(subject, "_", electrodes))

```


## Presentation


```{r presentation-noise-analysis}

presentation_split_encoding_elecs <- split_ofc_encoding_df_fdr %>%
  mutate(elec_ids = paste0(subject, "_", electrode)) %>%
  filter(perm_p_reg_fdr < 0.05 & perm_p_ttype_fdr < 0.05) %>%
  filter(epoch == "presentation" & predictor %in% c("self_var_payoff", "other_var_payoff"))


## Self Var Payoff 
elec_upper_conf <- NULL
elec_lower_conf <- NULL
pres_self_split_encoding_elecs <- presentation_split_encoding_elecs %>% filter(predictor == "self_var_payoff")

# run t test on residuals in both trial types
for(elec_id in unique(pres_self_split_encoding_elecs$elec_ids)){

    adv_df <- all_brain_data_pres %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Advantageous")
    
    dis_df <- all_brain_data_pres %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Disadvantageous")
    
    nBins <- colnames(all_brain_data_pres %>% select(starts_with("bin_")))[1:15]
    
    adv_resid <- NULL
    dis_resid <- NULL
    for(bin in nBins) {
      
      # run adv models #
      adv_bin_vec <- adv_df %>% pull(bin)
      adv_reg_vec <- adv_df %>% pull(other_var_payoff)
      adv_model <- summary(lm(adv_bin_vec ~ adv_reg_vec))
      adv_resid[bin] <- abs(median(adv_model$residuals))
      
      # run dis models #
      dis_bin_vec <- dis_df %>% pull(bin)
      dis_reg_vec <- dis_df %>% pull(other_var_payoff)
      dis_model <- summary(lm(dis_bin_vec ~ dis_reg_vec))
      dis_resid[bin] <- abs(median(dis_model$residuals))
      
    }
    
    t_results <- t.test(dis_resid, adv_resid)
    elec_upper_conf[elec_id] <- t_results$conf.int[2]
    elec_lower_conf[elec_id] <- t_results$conf.int[1]

}

elec_noise_pres_self_df <- as_tibble(cbind("elec_ids" = unique(pres_self_split_encoding_elecs$elec_ids), 
                                       elec_lower_conf, elec_upper_conf))
elec_noise_pres_self_df$predictor <- "self_var_payoff"

## Other Var Payoff 
elec_upper_conf <- NULL
elec_lower_conf <- NULL
pres_self_split_encoding_elecs <- presentation_split_encoding_elecs %>% filter(predictor == "other_var_payoff")

# run t test on residuals in both trial types
for(elec_id in unique(pres_self_split_encoding_elecs$elec_ids)){

    adv_df <- all_brain_data_pres %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Advantageous")
    
    dis_df <- all_brain_data_pres %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Disadvantageous")
    
    nBins <- colnames(all_brain_data_pres %>% select(starts_with("bin_")))[1:15]
    
    adv_resid <- NULL
    dis_resid <- NULL
    for(bin in nBins) {
      
      # run adv models #
      adv_bin_vec <- adv_df %>% pull(bin)
      adv_reg_vec <- adv_df %>% pull(other_var_payoff)
      adv_model <- summary(lm(adv_bin_vec ~ adv_reg_vec))
      adv_resid[bin] <- abs(median(adv_model$residuals))
      
      # run dis models #
      dis_bin_vec <- dis_df %>% pull(bin)
      dis_reg_vec <- dis_df %>% pull(other_var_payoff)
      dis_model <- summary(lm(dis_bin_vec ~ dis_reg_vec))
      dis_resid[bin] <- abs(median(dis_model$residuals))
      
    }
    
    t_results <- t.test(dis_resid, adv_resid)
    elec_upper_conf[elec_id] <- t_results$conf.int[2]
    elec_lower_conf[elec_id] <- t_results$conf.int[1]

}

elec_noise_pres_other_df <- as_tibble(cbind("elec_ids" = unique(pres_self_split_encoding_elecs$elec_ids), 
                                       elec_lower_conf, elec_upper_conf))
elec_noise_pres_other_df$predictor <- "other_var_payoff"

# combine dfs #
elec_noise_pres_df <- rbind(elec_noise_pres_self_df, elec_noise_pres_other_df)

```

## Pre-choice

Two pre-choice electrodes look like they are driven by a difference in noise-- so need to remove them!

`GP51_OFG26` & `GP51_OFG16`

```{r pre-choice-noise-analysis}

pre_choice_split_encoding_elecs <- split_ofc_encoding_df_fdr %>%
  mutate(elec_ids = paste0(subject, "_", electrode)) %>%
  filter(perm_p_reg_fdr < 0.05 & perm_p_ttype_fdr < 0.05) %>%
  filter(epoch == "pre-choice" & predictor %in% c("self_var_payoff", "other_var_payoff"))

prech_self_split_encoding_elecs <- pre_choice_split_encoding_elecs %>% filter(predictor == "self_var_payoff")

## Self Var Payoff
elec_upper_conf <- NULL
elec_lower_conf <- NULL
for(elec_id in unique(prech_self_split_encoding_elecs$elec_ids)){

    adv_df <- all_brain_data_pre_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Advantageous")
    
    dis_df <- all_brain_data_pre_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Disadvantageous")
    
    nBins <- nBins <- colnames(all_brain_data_pre_choice %>% select(starts_with("pre_")))
    
    adv_resid <- NULL
    dis_resid <- NULL
    for(bin in nBins) {
      
      # run adv models #
      adv_bin_vec <- adv_df %>% pull(bin)
      adv_reg_vec <- adv_df %>% pull(other_var_payoff)
      adv_model <- summary(lm(adv_bin_vec ~ adv_reg_vec))
      adv_resid[bin] <- abs(median(adv_model$residuals))
      
      # run dis models #
      dis_bin_vec <- dis_df %>% pull(bin)
      dis_reg_vec <- dis_df %>% pull(other_var_payoff)
      dis_model <- summary(lm(dis_bin_vec ~ dis_reg_vec))
      dis_resid[bin] <- abs(median(dis_model$residuals))
      
    }
    
    t_results <- t.test(dis_resid, adv_resid)
    elec_upper_conf[elec_id] <- t_results$conf.int[2]
    elec_lower_conf[elec_id] <- t_results$conf.int[1]

}

elec_noise_prech_self_df <- as_tibble(cbind("elec_ids" = unique(prech_self_split_encoding_elecs$elec_ids), 
                                       elec_lower_conf, elec_upper_conf))
elec_noise_prech_self_df$predictor <- "self_var_payoff"

## Other Var Payoff 
elec_upper_conf <- NULL
elec_lower_conf <- NULL
prech_other_split_encoding_elecs <- pre_choice_split_encoding_elecs %>% filter(predictor == "other_var_payoff")

# run t test on residuals in both trial types
for(elec_id in unique(prech_other_split_encoding_elecs$elec_ids)){

    adv_df <- all_brain_data_pre_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Advantageous")
    
    dis_df <- all_brain_data_pre_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Disadvantageous")
    
    nBins <- nBins <- colnames(all_brain_data_pre_choice %>% select(starts_with("pre_")))
    
    adv_resid <- NULL
    dis_resid <- NULL
    for(bin in nBins) {
      
      # run adv models #
      adv_bin_vec <- adv_df %>% pull(bin)
      adv_reg_vec <- adv_df %>% pull(other_var_payoff)
      adv_model <- summary(lm(adv_bin_vec ~ adv_reg_vec))
      adv_resid[bin] <- abs(median(adv_model$residuals))
      
      # run dis models #
      dis_bin_vec <- dis_df %>% pull(bin)
      dis_reg_vec <- dis_df %>% pull(other_var_payoff)
      dis_model <- summary(lm(dis_bin_vec ~ dis_reg_vec))
      dis_resid[bin] <- abs(median(dis_model$residuals))
      
    }
    
    t_results <- t.test(dis_resid, adv_resid)
    elec_upper_conf[elec_id] <- t_results$conf.int[2]
    elec_lower_conf[elec_id] <- t_results$conf.int[1]

}

elec_noise_prech_other_df <- as_tibble(cbind("elec_ids" = unique(prech_other_split_encoding_elecs$elec_ids), 
                                       elec_lower_conf, elec_upper_conf))
elec_noise_prech_other_df$predictor <- "other_var_payoff"

# combine dfs #
elec_noise_prech_df <- rbind(elec_noise_prech_self_df, elec_noise_prech_other_df)


```


## post-choice

`ST40_FG40` & `GP51_OFG41` & `GP51_OFG39` & `GP51_OFG11`

```{r post-choice-noise-analysis}

post_choice_split_encoding_elecs <- split_ofc_encoding_df_fdr %>%
  mutate(elec_ids = paste0(subject, "_", electrode)) %>%
  filter(perm_p_reg_fdr < 0.05 & perm_p_ttype_fdr < 0.05) %>%
  filter(epoch == "post-choice" & predictor %in% c("self_var_payoff", "other_var_payoff"))

post_self_split_encoding_elecs <- post_choice_split_encoding_elecs %>% filter(predictor == "self_var_payoff")

## Self Var Payoff
elec_upper_conf <- NULL
elec_lower_conf <- NULL
for(elec_id in unique(post_self_split_encoding_elecs$elec_ids)){

    adv_df <- all_brain_data_post_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Advantageous")
    
    dis_df <- all_brain_data_post_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Disadvantageous")
    
    nBins <- nBins <- colnames(all_brain_data_post_choice %>% select(starts_with("post_")))[1:20]
    
    adv_resid <- NULL
    dis_resid <- NULL
    for(bin in nBins) {
      
      # run adv models #
      adv_bin_vec <- adv_df %>% pull(bin)
      adv_reg_vec <- adv_df %>% pull(other_var_payoff)
      adv_model <- summary(lm(adv_bin_vec ~ adv_reg_vec))
      adv_resid[bin] <- abs(median(adv_model$residuals))
      
      # run dis models #
      dis_bin_vec <- dis_df %>% pull(bin)
      dis_reg_vec <- dis_df %>% pull(other_var_payoff)
      dis_model <- summary(lm(dis_bin_vec ~ dis_reg_vec))
      dis_resid[bin] <- abs(median(dis_model$residuals))
      
    }
    
    t_results <- t.test(dis_resid, adv_resid)
    elec_upper_conf[elec_id] <- t_results$conf.int[2]
    elec_lower_conf[elec_id] <- t_results$conf.int[1]

}

elec_noise_post_self_df <- as_tibble(cbind("elec_ids" = unique(post_self_split_encoding_elecs$elec_ids), 
                                       elec_lower_conf, elec_upper_conf))
elec_noise_post_self_df$predictor <- "self_var_payoff"

## Other Var Payoff 
elec_upper_conf <- NULL
elec_lower_conf <- NULL
post_other_split_encoding_elecs <- post_choice_split_encoding_elecs %>% filter(predictor == "other_var_payoff")

# run t test on residuals in both trial types
for(elec_id in unique(post_other_split_encoding_elecs$elec_ids)){

    adv_df <- all_brain_data_post_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Advantageous")
    
    dis_df <- all_brain_data_post_choice %>% 
      filter(elec_ids == elec_id) %>%
      filter(trial_type == "Disadvantageous")
    
    nBins <- nBins <- colnames(all_brain_data_post_choice %>% select(starts_with("post_")))[1:20]
    
    adv_resid <- NULL
    dis_resid <- NULL
    for(bin in nBins) {
      
      # run adv models #
      adv_bin_vec <- adv_df %>% pull(bin)
      adv_reg_vec <- adv_df %>% pull(other_var_payoff)
      adv_model <- summary(lm(adv_bin_vec ~ adv_reg_vec))
      adv_resid[bin] <- abs(median(adv_model$residuals))
      
      # run dis models #
      dis_bin_vec <- dis_df %>% pull(bin)
      dis_reg_vec <- dis_df %>% pull(other_var_payoff)
      dis_model <- summary(lm(dis_bin_vec ~ dis_reg_vec))
      dis_resid[bin] <- abs(median(dis_model$residuals))
      
    }
    
    t_results <- t.test(dis_resid, adv_resid)
    elec_upper_conf[elec_id] <- t_results$conf.int[2]
    elec_lower_conf[elec_id] <- t_results$conf.int[1]

}

elec_noise_post_other_df <- as_tibble(cbind("elec_ids" = unique(post_other_split_encoding_elecs$elec_ids), 
                                       elec_lower_conf, elec_upper_conf))
elec_noise_post_other_df$predictor <- "other_var_payoff"

# combine dfs #
elec_noise_post_df <- rbind(elec_noise_post_self_df, elec_noise_post_other_df)


```


## combined

```{r combined-epochs}

elec_noise_df <- rbind(elec_noise_pres_df %>% mutate(epoch = "presentation"),
                       elec_noise_prech_df %>% mutate(epoch = "pre-choice"),
                       elec_noise_post_df %>% mutate(epoch = "post-choice"))

# sig diff in noise
elec_noise_df <- elec_noise_df %>%
  mutate(noise_diff = if_else(0 > elec_lower_conf & 0 < elec_upper_conf, 0, 1)) %>%
  mutate(elec_epoch_ids = paste(elec_ids, epoch, sep = "_"))

trial_dep_noise_df <- elec_noise_df %>%
  filter(noise_diff == 1)

# save #
write_csv(trial_dep_noise_df, path(here(), "results", "trial_dep_differences_noise.csv"))

```


