---
title: "Null Distribution ~ Residuals"
output: html_document
date: '2022-12-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 5,  # set default width of figures
  fig.height <- 8,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
# library(ggthemr)
# library(grid)
# library(gtable)
# library(gridExtra)
# library(wesanderson)
# library(ggsci)
# library(zoo)
# library(kableExtra)
# library(lme4)
# library(RColorBrewer)
# library(doParallel)
# library(parallel)
# library(foreach)
library(here)
library(fs)
# library(ggcorrplot)
# library(viridis)
# library(lmtest)
# library(gt)
# library(ggalluvial)
# library(parameters)
# library(factoextra)
# library(NbClust)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "load_and_collate_reg_results.R"))

# quick necessary function
comb <- function(x, ...) {  
      mapply(rbind,x,...,SIMPLIFY=FALSE)}


# ## parallelization ##
# nCores <- 4
# registerDoParallel(nCores)
#


#find . -type f -mtime +10 -maxdepth 1 -exec mv {} before_3-21-21 \;
```


# Null Distributions (Residuals)

We calculated the full null distributions for both types of permutation in the inequity-dependent analyses. The first type shuffled the regressor within each inequity type. In the second type we shuffled the inequity type labels. As part of sanity checking our work, we did some visualizations of the null distribution to make sure that we did not see the inequity dependent effect within the null distribution (an old version of the analysis involved a clustering approach that was based on a mistake in logic, which I only realized by looking through the null distribution). 

For these reasons, we chose to calculate and save out the null distribution rather than calculating the permutation statistic for each permute. However, this is memory intensive and the files are large an unwieldy. Wouldn't recommend this if you do not need the null distribution.

Also requires the output of `compile_split_regression_results.Rmd`

## Prep Real Data


```{r prep-real-data}

# load  split data #
dis_only_ofc_results <- read_csv(
  path(here(), "results", "single_regressions", "dis_only_ofc_residual_ogpermutation_single_regressions_12_1_2022.csv"),
  col_types = cols())
adv_only_ofc_results <- read_csv(
  path(here(), "results", "single_regressions", "adv_only_ofc_residual_ogpermutation_single_regressions_12_1_2022.csv"),
  col_types = cols())
split_new_results <- rbind(dis_only_ofc_results %>% mutate(state = "Disadvantageous"),
                           adv_only_ofc_results %>% mutate(state = "Advantageous"))
split_ofc_results <- split_new_results %>% mutate(predictor = gsub("^FG_", "", predictor))

num_of_elecs <- split_ofc_results %>% 
  select(subject, electrode) %>%
  distinct()

write_csv(split_ofc_test_stats, path(here(), "results", "single_regressions", "compiled_ofc_residual_ogpermutation_single_regressions_12_1_2022.csv"))

```

## permute on regressors

### compile null distributions

```{r load-null-dist-data, eval=FALSE}

## get all the csvs in the null folder ##
filenames <- dir(path(here(), "results", "null_resids_average_r2"))
# separate adv and dis #
adv_files <- filenames[grepl("*null-average-r2-adv", filenames)]
dis_files <- filenames[grepl("*null-average-r2-dis", filenames)]

adv_null_results <- NULL
for(file in adv_files){
  tmp <- read_csv(path(here(), "results", "null_resids_average_r2", file))
  tmp$state <- "Advantageous"
  tmp$freq <- "theta"
  if(grepl("pres-", file)) {
    tmp$epoch <- "presentation"
  } else if(grepl("pre-choice", file)) {
    tmp$epoch <- "pre-choice"
  } else {
    tmp$epoch <- "post-choice"
  }

  if(is.null(adv_null_results)) {
    adv_null_results <- tmp
  } else {
    adv_null_results <- rbind(adv_null_results, tmp)
  }

}

dis_null_results <- NULL
for(file in dis_files){
  tmp <- read_csv(path(here(), "results", "null_resids_average_r2", file))
  tmp$state <- "Disadvantageous"
  tmp$freq <- "theta"
  if(grepl("pres-", file)) {
    tmp$epoch <- "presentation"
  } else if(grepl("pre-choice", file)) {
    tmp$epoch <- "pre-choice"
  } else {
    tmp$epoch <- "post-choice"
  }

  if(is.null(dis_null_results)) {
    dis_null_results <- tmp
  } else {
    dis_null_results <- rbind(dis_null_results, tmp)
  }

}


complete_null_results <- rbind(dis_null_results, adv_null_results)
write_csv(complete_null_results, path(here(), "results", "null_resids_average_r2",
                                      "compiled_null_resids_results_ogpermutation_1_2_23.csv"))
```

### create new test statistic

```{r test-stat}

complete_null_results <- read_csv(path(here(), "results", "null_resids_average_r2",
                                       "compiled_null_resids_results_ogpermutation_1_2_23.csv"))

# sort to create permutation index #
complete_null_results_sorted <- complete_null_results %>%
  arrange(subject, electrode, epoch, predictor, state)

remove(complete_null_results)

# create permutation index #
complete_null_results_sorted_post <- complete_null_results_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'post-choice') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids, state) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 20))))

complete_null_results_sorted_pre <- complete_null_results_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'pre-choice') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids, state) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 13))))

complete_null_results_sorted_pres <- complete_null_results_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'presentation') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids, state) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 15))))

complete_null_results_prepped <- rbind(complete_null_results_sorted_pres,
                                       complete_null_results_sorted_pre,
                                       complete_null_results_sorted_post)

remove(complete_null_results_sorted_post)
remove(complete_null_results_sorted_pre)
remove(complete_null_results_sorted_pres)


## original r2 version ##
null_test_stat_df <- complete_null_results_prepped %>%
  select(-Beta, -p, -elec_ids) %>%
  mutate(permute_id = paste(subject, electrode, predictor, epoch, permutation, sep = "_")) %>%
  group_by(permute_id) %>%
  pivot_wider(names_from = state, values_from = R2) %>%
  mutate(test_stat = abs(sum(Disadvantageous - Advantageous ))) %>%
  # for flow plot #
  mutate(adv_only_test_stat = abs(sum(Advantageous))) %>%
  mutate(dis_only_test_stat = abs(sum(Disadvantageous))) %>%
  select(subject, electrode, predictor, epoch, permutation, permute_id, test_stat, adv_only_test_stat, dis_only_test_stat) %>%
  distinct() %>%
  mutate(electrode = gsub("POL ", "", electrode)) %>%
  mutate(electrode = gsub(" POL", "", electrode)) %>%
  mutate(electrode = gsub("-Ref", "", electrode)) %>%
  mutate(electrode = gsub("-Ref-", "-", electrode)) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_"))


```

```{r findp-values}

true_ofc_split_results <- read_csv('results/single_regressions/compiled_ofc_residual_ogpermutation_single_regressions_12_1_2022.csv')

split_true_ofc_tstats <- true_ofc_split_results %>%
  # fix weird parsing issue in this run that occured due to lack of freq in tag
  mutate(predictor = if_else(grepl("other", predictor), "other_var_payoff", if_else(grepl("self", predictor), "self_var_payoff", "error"))) %>%
  filter(predictor %in% c("self_var_payoff", "other_var_payoff", "max", "min")) %>%
  select(subject, electrode, predictor, epoch, R2, bin, state, ROI) %>%
  mutate(elec_id = paste(subject, electrode, sep = "_")) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(reg_id) %>%
  pivot_wider(names_from = state, values_from = R2) %>%
  mutate(test_stat_real = abs(sum(Disadvantageous - Advantageous ))) %>%
  mutate(adv_only_test_stat_real = abs(sum(Advantageous))) %>%
  mutate(dis_only_test_stat_real = abs(sum(Disadvantageous)))

pval_permuted <- NULL   
adv_permuted <- NULL
dis_permuted <- NULL
subs <- unique(split_true_ofc_tstats$subject)
#pval_permuted <- foreach(h = 1:length(subs), .inorder=FALSE, .combine = 'comb', .multicombine=TRUE) %dopar% {
#  sub <- subs[h]

for(sub in subs) {
  print(sub)
  sub_tmp <- null_test_stat_df %>%
    filter(subject == sub)


  for(pred in unique(split_true_ofc_tstats$predictor)) {

    pred_tmp <- sub_tmp %>% filter(predictor == pred)

    id_tmp <- split_true_ofc_tstats %>%
      filter(predictor == pred & subject == sub)

    for(id in unique(id_tmp$reg_id)){

      tmp <-   split_true_ofc_tstats %>%
        filter(reg_id == id)


      tmp_null <- pred_tmp %>%
        filter(reg_id == id)

      pval_permuted[id] <- sum(tmp_null$test_stat > unique(tmp$test_stat_real))/1000
      adv_permuted[id] <- sum(tmp_null$adv_only_test_stat > unique(tmp$adv_only_test_stat_real))/1000
      dis_permuted[id] <- sum(tmp_null$dis_only_test_stat > unique(tmp$dis_only_test_stat_real))/1000

    }
  }
}  



pval_permuted_df <- data.frame("permuted_p" = pval_permuted, "adv_pval" = adv_permuted, "dis_pval" = dis_permuted, "reg_id" = names(pval_permuted))

split_true_ofc_tstats_wpvals <- merge.data.frame(split_true_ofc_tstats, pval_permuted_df, by = "reg_id")

write_csv(split_true_ofc_tstats_wpvals, 'results/single_regressions/compiled_ofc_resid_ogpermutation_wpvalues_single_regressions_12_1_2022.csv')
```

```{r cut-off-point}

cutoff_df_full <- null_test_stat_df %>%
  ungroup() %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(reg_id) %>%
  select(reg_id, subject, electrode, predictor, epoch, test_stat) %>%
  distinct() %>%
  slice_max(test_stat, n = 50)

cutoff_df <- cutoff_df_full %>%
  slice_min(test_stat, n = 1)


write_csv(cutoff_df, path(here(), "results", "null_resids_average_r2", 
                          "adv_dis_resid_r2_sig_difference_test_stat_12_1_2022.csv"))

write_csv(cutoff_df_full, path(here(), "results", "null_resids_average_r2",
                               "adv_dis_resid_r2_sig_difference_test_stat_top50_12_1_2022.csv"))



```


# Trial Type Permutations

## permute on trial labels

### compile null distributions

```{r load-null-ttype-dist-data, eval=FALSE}

## get all the csvs in the null folder ##
filenames <- dir(path(here(), "results", "null_resids_ttype"))
# separate adv and dis #
ttype_files <- filenames[grepl("*ttype-permute-cperm-hilbertRS", filenames)]

null_ttype_df <- NULL
for(file in ttype_files){
  tmp <- read_csv(path(here(), "results", "null_resids_ttype", file))
  if(grepl("pres-", file)) {
    tmp$epoch <- "presentation"
  } else if(grepl("pre-choice", file)) {
    tmp$epoch <- "pre-choice"
  } else {
    tmp$epoch <- "post-choice"
  }

  if(is.null(null_ttype_df)) {
    null_ttype_df <- tmp
  } else {
    null_ttype_df <- rbind(null_ttype_df, tmp)
  }

}

write_csv(null_ttype_df, path(here(), "results", "null_resids_ttype",
                              "compiled_null_resids_ttype_results_1_2_23.csv"))
```

### create new test statistic

```{r test-stat}

# null_ttype_df <- read_csv(path(here(), "results", "null_resids_ttype",
#                                "compiled_null_resids_ttype_results_10_15_22.csv"))

# sort to create permutation index #
null_ttype_df_sorted <- null_ttype_df %>%
  arrange(subject, electrode, epoch, predictor)

remove(null_ttype_df)

# create permutation index #
null_ttype_df_sorted_post <- null_ttype_df_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'post-choice') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 20))))

null_ttype_df_sorted_pre <- null_ttype_df_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'pre-choice') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 13))))

null_ttype_df_sorted_pres <- null_ttype_df_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'presentation') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 15))))

null_ttype_df_prepped <- rbind(null_ttype_df_sorted_pres,
                                       null_ttype_df_sorted_pre,
                                       null_ttype_df_sorted_post)

remove(null_ttype_df_sorted_pres)
remove(null_ttype_df_sorted_pre)
remove(null_ttype_df_sorted_post)

null_ttype_df_prepped_adv <- null_ttype_df_prepped %>%
  select(subject, electrode, predictor, epoch, permutation, elec_ids, bin, R2_Adv, Beta_Adv, p_Adv) %>%
  mutate(state = "Advantageous") %>%
  rename(R2 = R2_Adv) %>%
  rename(Beta = Beta_Adv) %>%
  rename(p = p_Adv)

null_ttype_df_prepped_dis <- null_ttype_df_prepped %>%
  select(subject, electrode, predictor, epoch, permutation, elec_ids, bin, R2_Dis, Beta_Dis, p_Dis) %>%
  mutate(state = "Disadvantageous") %>%
  rename(R2 = R2_Dis) %>%
  rename(Beta = Beta_Dis) %>%
  rename(p = p_Dis)

null_ttype_df_prepped <- rbind(null_ttype_df_prepped_adv, null_ttype_df_prepped_dis)

remove(null_ttype_df_prepped_adv)
remove(null_ttype_df_prepped_dis)



null_ttype_test_stat_df <- null_ttype_df_prepped %>%
  select(-Beta, -p, -elec_ids) %>%
  mutate(permute_id = paste(subject, electrode, predictor, epoch, permutation, sep = "_")) %>%
  group_by(permute_id) %>%
  pivot_wider(names_from = state, values_from = R2) %>%
  mutate(test_stat = abs(sum(Disadvantageous - Advantageous ))) %>%
  select(subject, electrode, predictor, epoch, permutation, permute_id, test_stat) %>%
  distinct() %>%
  mutate(electrode = gsub("POL ", "", electrode)) %>%
  mutate(electrode = gsub(" POL", "", electrode)) %>%
  mutate(electrode = gsub("-Ref", "", electrode)) %>%
  mutate(electrode = gsub("-Ref-", "-", electrode)) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_"))


# null_ttype_test_stat_df %>%
#   ggplot(., aes(x = test_stat)) +
#   geom_histogram(binwidth = .01, alpha = .7) +
#   theme(panel.background = element_rect(fill = "white"))

```


```{r findp-values}

true_ofc_split_results <- read_csv('results/single_regressions/compiled_ofc_residual_ogpermutation_single_regressions_12_1_2022.csv')

split_true_ofc_tstats <- true_ofc_split_results %>%
  # fix weird parsing issue in this run that occured due to lack of freq in tag
  mutate(predictor = if_else(grepl("other", predictor), "other_var_payoff", if_else(grepl("self", predictor), "self_var_payoff", "error"))) %>%
  filter(predictor %in% c("self_var_payoff", "other_var_payoff", "max", "min")) %>%
  select(subject, electrode, predictor, epoch, R2, bin, state, ROI) %>%
  mutate(elec_id = paste(subject, electrode, sep = "_")) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(reg_id) %>%
  pivot_wider(names_from = state, values_from = R2) %>%
  mutate(test_stat_real = abs(sum(Disadvantageous - Advantageous )))

  comb <- function(x, ...) {  
        mapply(rbind,x,...,SIMPLIFY=FALSE)}

pval_permuted <- NULL      
subs <- unique(split_true_ofc_tstats$subject)

for(sub in subs) {
  print(sub)
  sub_tmp <- null_ttype_test_stat_df %>%
    filter(subject == sub)


  for(pred in unique(split_true_ofc_tstats$predictor)) {

    pred_tmp <- sub_tmp %>% filter(predictor == pred)

    id_tmp <- split_true_ofc_tstats %>%
      filter(predictor == pred & subject == sub)

    for(id in unique(id_tmp$reg_id)){

      tmp <-   split_true_ofc_tstats %>%
        filter(reg_id == id)


      tmp_null <- pred_tmp %>%
        filter(reg_id == id)

      pval_permuted[id] <- sum(tmp_null$test_stat > unique(tmp$test_stat_real))/1000  

    }
  }
}  



pval_permuted_df <- data.frame("permuted_p" = pval_permuted, "reg_id" = names(pval_permuted))

split_true_ofc_tstats_wpvals <- merge.data.frame(split_true_ofc_tstats, pval_permuted_df, by = "reg_id")

write_csv(split_true_ofc_tstats_wpvals, 'results/single_regressions/compiled_ofc_resids_ogpermutation_ttype_wpvalues_single_regressions_12_1_2022.csv')
```

```{r cut-off-point}

cutoff_ttype_full <- null_ttype_test_stat_df %>%
  ungroup() %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(reg_id) %>%
  select(reg_id, subject, electrode, predictor, epoch, test_stat) %>%
  distinct() %>%
  slice_max(test_stat, n = 50)


cutoff_ttype_df <- cutoff_ttype_full %>%
  slice_min(test_stat, n = 1)



write_csv(cutoff_ttype_df, path(here(), "results", "null_resids_ttype",
                                "ttype_difference_resids_test_stat_12_1_2022.csv"))

write_csv(cutoff_ttype_full, path(here(), "results", "null_resids_ttype",
                                "ttype_difference_resids_test_stat_top_50_12_1_2022.csv"))
```

Stopped here at neuro conference

### comparison of trial type and regressor permuting

```{r cutoff-compare}

cutoff_ttype_full$permutation_type <- "ttype"
cutoff_ttype_full<- cutoff_ttype_full %>%
  group_by(reg_id) %>%
  mutate(permute_id = 1:50)


cutoff_df_full$permutation_type <- "regressor"
cutoff_df_full<- cutoff_df_full %>%
  group_by(reg_id) %>%
  mutate(permute_id = 1:50)

cutoff_compare_full <- rbind(cutoff_ttype_full, cutoff_df_full )

fals_pos_df <- cutoff_compare_full %>%
  group_by(reg_id, permutation_type) %>%
  mutate(cutt_off = min(test_stat)) %>%
  pivot_wider(names_from = permutation_type, values_from =  c(cutt_off, test_stat))


write_csv(fals_pos_df, path(here(), "results", "null_average_r2", "p_val_lookup_theta_df_new.csv"))


## look at distributions
cutoff_ttype_df$permutation_type <- "ttype"
cutoff_df$permutation_type <- "regressor"

cutoff_compare_df <- rbind(cutoff_ttype_df, cutoff_df )

real_data_for_dist_compare <- split_ofc_test_stats %>%
  select(reg_id, test_stat_real) %>%
  distinct()


cutoff_compare_df %>%
  ggplot(.) +
  geom_histogram(alpha =  .5, binwidth = .01, aes(x = test_stat, fill = permutation_type, y = stat(width*density))) +
  geom_histogram(data = real_data_for_dist_compare,
                 alpha = .5, fill = 'purple', binwidth = .01, aes(x = test_stat_real, y = stat(width*density))) +
  scale_y_continuous(labels = scales::percent_format()) +
  theme(panel.background = element_rect(fill = "white"))


```




### EDA

```{r eda-ofg51}

null_test_stat_df <- complete_null_results_prepped %>%
  select(-X1) %>%
  mutate(permute_id = paste(subject, electrode, predictor, epoch, permutation, sep = "_")) %>%
  group_by(permute_id) %>%
  pivot_wider(names_from = state, values_from = c(R2, Beta, p))


null_test_stat_df <- null_test_stat_df %>%
  mutate(test_stat = sum(abs(R2_Disadvantageous - R2_Advantageous )))

tmp_ofg51_null <- null_test_stat_df %>%
  filter(subject == "GP51" & electrode == "OFG51" & predictor == "other_var_payoff" & epoch == "presentation") %>%
  filter(test_stat > 0.6175786) %>%
  select(bin, permute_id, permutation, Beta_Advantageous, Beta_Disadvantageous) %>%
  pivot_longer(cols = starts_with("Beta_"), names_to = "State", values_to = "Beta")

tmp_ofg51_null %>%
  # pivot_longer(cols = c(Disadvantageous, Advantageous), names_to = "state", values_to = "R2") %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  ggplot(., aes(x = time, y = Beta, color = State)) +
  geom_point() +
  geom_line() +
  ylim(-.02, .02) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~permutation)

```



##  EDA from earlier versions


```{r quick-vis}

complete_null_results_sorted <- complete_null_results %>%
  arrange(subject, electrode, epoch, predictor, state)

complete_null_results_sorted_post <- complete_null_results_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'post-choice') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids, state) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 20))))

complete_null_results_sorted_pre <- complete_null_results_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'pre-choice') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids, state) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 13))))

complete_null_results_sorted_pres <- complete_null_results_sorted %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  filter(epoch == 'presentation') %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids, state) %>%
  mutate(permutation = unlist(lapply(1:1000, FUN = function(x) rep(x, 15))))

complete_null_results_prepped <- rbind(complete_null_results_sorted_pres,
                                       complete_null_results_sorted_pre,
                                       complete_null_results_sorted_post)

null_r2_df <- complete_null_results_prepped %>%
    filter(predictor %in% c("max")) %>%
    group_by(elec_ids, state, permutation) %>%
    filter(p < 0.05) %>%
    mutate(dummy = 50) %>%
    mutate(encode_duration = sum(dummy)) %>%
    mutate(average_r2 = encode_duration * mean(R2))

null_r2_df_wide <- null_r2_df %>%
    select(average_r2, bin, state, elec_ids) %>%
    distinct() %>%
    ungroup() %>%
    pivot_wider(names_from = state, values_from = average_r2, values_fill = 0) %>%
    select(elec_ids, bin, Advantageous, Disadvantageous)

null_plot <- null_r2_df_wide %>%
  ggplot(., aes(x = Advantageous, y = Disadvantageous,)) +
  geom_point(size = 1, alpha = .3, color = 'grey') +
  theme(panel.background = element_rect(fill = "white")) +
  ggtitle('null dist')

null_r2_df_wide %>%
  ggplot(., aes(x = Advantageous, y = Disadvantageous,)) +
  geom_point(size = 1, alpha = .01, color = 'grey') +
  geom_jitter(data = all_r2_cluster_df,
              aes(x = Advantageous, y = Disadvantageous), size = 2, color = '#9B59B6') +
  theme(panel.background = element_rect(fill = "white")) +
  ggtitle('null dist + real average encoding')

```

```{r individual-r2-plots}

example_elec <- split_ofc_results %>%
  filter(subject == "GP51" & electrode == "OFG2" & predictor == "other_var_payoff" & epoch == "presentation") %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  select(time, R2, state)

example_elec %>%
  ggplot(., aes(x = time, y = R2, color = state)) +
  geom_point(alpha = 1) +
  geom_line(alpha = 1) +
  ylim(0, .1) +
  theme(panel.background = element_rect(fill = "white"))

null_examples <- complete_null_results_prepped %>%
  filter(subject == "GP51" & electrode == "OFG2" & predictor == "other_var_payoff" & epoch == "presentation") %>%
  mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
  select(time, R2, state, permutation, elec_ids)

null_examples %>%
  filter(permutation %in% sample(1:1000, 1)) %>%
  ggplot(., aes(x = time, y = R2, color = state, group = permutation)) +
  geom_point(alpha = 1) +
  geom_line(alpha = 1) +
  ylim(0, .1) +
  theme(panel.background = element_rect(fill = "white"))

```

```{r sample-vec-cors}

reg_vec <- behave_data_GP51 %>%
  # filter(trial_type == "Disadvantageous") %>%
  filter(trial_type != "equality") %>%
  pull("other_var_payoff")

null_mat <- as.matrix(sapply(1:1000, function(x) sample(reg_vec)))
null_cor_full <- cor(null_mat)
# null_cor <- cor(null_mat)

mean(null_cor)
sd(null_cor)


mean(null_cor_full)
sd(null_cor_full)

```




```{r thresholding}

null_examples %>%
  group_by(permutation) %>%
  mutate(better_than_real = sum(R2 > 0.075)) %>%
  select(permutation, elec_ids, state, better_than_real) %>%
  distinct() %>%
  ggplot(aes(x = better_than_real)) +
  geom_histogram(binwidth = 1) +
  theme(panel.background = element_rect(fill = "white"))


tmp <- null_examples %>%
  group_by(permutation) %>%
  mutate(better_than_real = sum(R2 > 0.05)) %>%
  select(permutation, elec_ids, state, better_than_real) %>%
  distinct()



table(tmp$better_than_real >3)

```





```{r chi-square-tests}

split_ofc_table <- split_ofc_results %>%
  filter(predictor %in% c("max", "min", "self_var_payoff", "other_var_payoff")) %>%
  mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  group_by(elec_ids, state) %>%
  mutate(average_r2 = mean(R2)) %>%
  select(average_r2, state, elec_ids) %>%
  ungroup() %>%
  mutate(discrete_cut = if_else(average_r2 > .024, 1, 0)) %>%
  select(-average_r2) %>%
  distinct() %>%
  pivot_wider(names_from = state, values_from = discrete_cut)

complete_null_table <- complete_null_results %>%
  mutate(discrete_cut = if_else(Average_R2 > .024, 1, 0)) %>%
  mutate(perm_ids = paste(subject, electrode, predictor, epoch, X1, sep = "_")) %>%
  select(perm_ids, state, discrete_cut) %>%
  pivot_wider(names_from = state, values_from = discrete_cut) %>%
  mutate(upper_triangle = if_else(Advantageous +  Disadvantageous == 2, 1, 0))

total_null <- dim(complete_null_table)[1]
total_real <- dim(split_ofc_table)[1]


null_table <- table(complete_null_table$Disadvantageous, complete_null_table$Advantageous,
                    dnn = c("Dis.", "Adv."))
real_table <- table(split_ofc_table$Disadvantageous, split_ofc_table$Advantageous,
                    dnn = c("Dis.", "Adv."))

null_table/total_null * 135 * 12
real_table/total_real * 135 * 12


chisq.test(null_table, real_table)

table(complete_null_table$Disadvantageous)
table(complete_null_table$Advantageous)
```


```{r correlations}

real_correlations_df <- split_ofc_results %>%
      filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
      filter(p < 0.05) %>%
      mutate(elec_ids = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
      group_by(elec_ids, state) %>%
      mutate(average_r2 = mean(R2)) %>%
      select(average_r2, state, elec_ids, subject, electrode, predictor, epoch) %>%
      distinct() %>%
      ungroup() %>%
      pivot_wider(names_from = state, values_from = average_r2) %>%
      select(elec_ids, subject, electrode, predictor, epoch, Advantageous, Disadvantageous) %>%
      mutate(diff = (Advantageous - Disadvantageous)  )

null_correlations_df <- complete_null_results_wide %>%
      mutate(diff = (Advantageous - Disadvantageous) )

real_cor <- cor.test(real_correlations_df$Disadvantageous, real_correlations_df$Advantageous)

null_cor <- cor.test(null_correlations_df$Disadvantageous, null_correlations_df$Advantageous)

null_correlations_df <- null_correlations_df %>%
  filter(Advantageous > .01 | Disadvantageous > 0.01)

real_correlations_df <- real_correlations_df %>%
  filter(Advantageous > .01 | Disadvantageous > 0.01)

null_correlations_df %>%
  ggplot(., aes(x =diff, y = stat(density*width))) +
  geom_histogram(binwidth = .001, alpha = .5) +
  geom_histogram(data = real_correlations_df, aes(x = diff, y = stat(density*width)),
                 binwidth = .001, fill = 'red', alpha = .5) +
  xlim(-.2, .2) +
  theme(panel.background = element_rect(fill = "white"))

```


```{r other-var-chi-tables}

complete_null_table_otherv <- complete_null_table %>%
  filter(grepl("other_var_payoff", perm_ids))

split_ofc_table_otherv <- split_ofc_table %>%
  filter(grepl("other_var_payoff", elec_ids))

total_null <- dim(complete_null_table_otherv)[1]
total_real <- dim(split_ofc_table_otherv)[1]


null_table_otherv <- table(complete_null_table_otherv$Disadvantageous,
                           complete_null_table_otherv$Advantageous, dnn = c("Dis.", "Adv."))
real_table_otherv <- table(split_ofc_table_otherv$Disadvantageous,
                           split_ofc_table_otherv$Advantageous, dnn = c("Dis.", "Adv."))

null_table_otherv/total_null * 100
real_table_otherv/total_real * 100


```


```{r samples}

complete_null_results %>%
  filter(X1 %in% sample(X1, 200)) %>%
  pivot_wider(names_from = context_state, values_from = Average_R2) %>%
  ggplot(., aes(y = Advantageous, x = Disadvantageous)) +
  geom_point(alpha = .5) +
  # geom_hline(yintercept = .035, color = 'black') +
  # geom_vline(xintercept = .035, color = 'black') +
  theme(panel.background = element_rect(fill = "white"))

```


```{r 2dhist}


complete_null_results %>%
  # filter(X1 %in% sample(X1, 200)) %>%
  pivot_wider(names_from = state, values_from = Average_R2) %>%
  ggplot(., aes(y = Advantageous, x = Disadvantageous)) +
  geom_bin2d(bins = 200) +
  # geom_hline(yintercept = .035, color = 'black') +
  # geom_vline(xintercept = .035, color = 'black') +
  theme(panel.background = element_rect(fill = "white")) +
  scale_fill_viridis_c()


```
