---
title: "Split * Unified Encoding Overlap"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 5,  # set default width of figures
  fig.height <- 8,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
# library(summarytools)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(ggalluvial)
library(parameters)
library(factoextra)
library(NbClust)

## hand written functions ##
source(path(here(), "R", "load_behave_data.R"))
source(path(here(), "R", "prep_behave_data.R"))
source(path(here(), "R", "stretch_start_end.R"))
source(path(here(), "R", "load_high_gamma_data.R"))
source(path(here(), "R", "rolling_window_and_baseline.R"))
source(path(here(), "R", "compile_mult_reg_results.R"))
source(path(here(), "R", "compile_mult_reg_results.R"))
# source('~/Projects/nice_r_functions/ggpaired_pretty.R')
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "load_and_collate_reg_results.R"))



## plotting helpers ##
ggthemr("solarized")
getPalette = colorRampPalette(brewer.pal(9, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 4
# registerDoParallel(nCores)
# 


#find . -type f -mtime +10 -maxdepth 1 -exec mv {} before_3-21-21 \;
```


## Overlap between Split and Unified Encoding

There are two types of overlap to be an analyzed in this document. The first is when an electrode was marked as a unified encoding electrode, but this was really driven by such strong encoding in one trial type that it overcame the lack of effect in the other trial type. The second is when sn electrode as marked as a split encoding electrode, when it really was using a unified encoding scheme for a different predictor.


```{r load-data}
## split results ##
# load permuted regressor results #
split_ofc_encoding_reg_df <- read_csv(path(here(), "results", "single_regressions",
                                       "compiled_ofc_ogpermutation_wpvalues_single_regressions_1_28_2022.csv"))

# load permuted trial results #
split_ofc_encoding_ttype_df <- read_csv(path(here(), "results", "single_regressions",
                                       "compiled_ofc_ogpermutation_ttype_wpvalues_single_regressions_1_28_2022.csv"))

# rename test stats and combine #
split_ofc_encoding_reg_df <- split_ofc_encoding_reg_df %>%
  rename(test_stat_real_reg = test_stat_real) %>%
  rename(permuted_p_reg = permuted_p)

split_ofc_encoding_ttype_df <- split_ofc_encoding_ttype_df %>%
  rename(test_stat_real_ttype = test_stat_real) %>%
  rename(permuted_p_ttype = permuted_p)

split_ofc_encoding_df <- full_join(split_ofc_encoding_reg_df, split_ofc_encoding_ttype_df)


## unified results ##
unified_hfa_data <- read_csv(path(here(), "results", "single_regressions",
                                  "compiled_unified_ogpermutation_ofc_results_1_26_2022.csv"))

```


```{r prep-dfs}

## prep unified ##
unified_hfa_data_clean <- unified_hfa_data %>%
  mutate(elec_id = paste(subject, electrode, sep = "_")) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_")) 

unified_hfa_data_fdr <- unified_hfa_data_clean %>%
  select(reg_id, subject, electrode, predictor, epoch, perm_p) %>%
  distinct() %>%
  group_by(epoch, predictor) %>%
  mutate(perm_p_unified_fdr = p.adjust(perm_p, method = "fdr"))

## prep split ##
split_ofc_encoding_clean<- split_ofc_encoding_df %>%
  mutate(elec_id = paste(subject, electrode, sep = "_")) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_"))

split_ofc_encoding_fdr <- split_ofc_encoding_clean %>%
  select(reg_id, subject, electrode, predictor, epoch, permuted_p_reg, permuted_p_ttype) %>%
  distinct() %>%
  group_by(epoch, predictor) %>%
  mutate(perm_p_reg_fdr = p.adjust(permuted_p_reg, method = "fdr")) %>%
  mutate(perm_p_ttype_fdr = p.adjust(permuted_p_ttype, method = "fdr"))

## combine
hfa_encoding_df <- left_join(split_ofc_encoding_fdr, unified_hfa_data_fdr)



```


```{r load-raw-hfa-data, echo = F}

# load hfa data #
all_brain_data_pres <-  read_csv(path(here(), "/munge/all_brain_data_pres_1_3_2022.csv"), 
                                 col_types = cols())
all_brain_data_pre_choice <-  read_csv(path(here(), "/munge/all_brain_data_pre_choice_1_3_2022.csv"), 
                                       col_types = cols())
all_brain_data_post_choice <-  read_csv(path(here(), "/munge/all_brain_data_post_choice_1_3_2022.csv"),
                                        col_types = cols())

```


## Split encoding mischaracterized as Unified

```{r comparing-encoding-strats}

hfa_encoding_compare_df <- hfa_encoding_df %>%
  select(-perm_p) %>%
  filter(predictor %in% c("max", "min", "other_var_payoff", "self_var_payoff")) %>%
  mutate(overlap = if_else(perm_p_unified_fdr < 0.05 & perm_p_ttype_fdr < 0.05 & perm_p_reg_fdr < 0.05, "both", 
                           if_else(perm_p_ttype_fdr < 0.05 & perm_p_reg_fdr < 0.05, "split",
                                   if_else(perm_p_unified_fdr < 0.05, "unified", "neither")))) 

both_sig_df <- hfa_encoding_compare_df %>%
  filter(overlap == "both")

post_both_df <- both_sig_df %>%
  filter(epoch == "post-choice") 

for(sub in unique(post_both_df$subject)) {
  
  both_sig_sub <- post_both_df %>%
    filter(subject == sub) 
  
  for(elec in unique(both_sig_sub$electrode)) {
    
    both_sig_sub_elec <- both_sig_sub %>%
      filter(electrode == elec) 
    
    brain_behave_elec <- all_brain_data_post_choice %>%
      filter(subject == sub & electrodes == elec)
    
    for(pred in unique(both_sig_sub_elec$predictor)){
      
     adv_plot <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
         
       print(plot( arrangeGrob(grobs = list(adv_plot,dis_plot), nrow = 2, ncol = 1)))

      
      
    }

  }
  
}

```

```{r num-of-elecs}

both_sig_elecs <- both_sig_df %>%
  mutate(elec_ids = paste0(subject, "_", electrode)) %>%
  mutate(reg_id = paste(subject, electrode, predictor, epoch, sep = "_")) %>%
  pull(reg_id)

```




## Unified encoding mischaracterized as Split

self, adv => max
self, dis => min

other, dis => max
other, adv => min

```{r prep-dfs-2}

scatter_plot_r2_df <- split_ofc_encoding_df %>%
  group_by(reg_id) %>%
  mutate(mean_adv = mean(Advantageous)) %>%
  mutate(mean_dis = mean(Disadvantageous)) %>%
  select(mean_adv, mean_dis, reg_id) %>%
  distinct() 

scatter_plot_r2_fdr_df <- left_join(scatter_plot_r2_df, split_ofc_encoding_fdr)


scatter_plot_r2_fdr_df <- scatter_plot_r2_fdr_df %>%
  mutate(sig = if_else(mean_dis > mean_adv & perm_p_reg_fdr < 0.05 & perm_p_ttype_fdr < 0.05, "Disadvantageous", 
                       if_else(mean_adv >= mean_dis & perm_p_reg_fdr < 0.05 & perm_p_ttype_fdr < 0.05, "Advantegous",
                               "Not Sig.")))


```

### Unified Max Encoding

```{r  unified-max}

max_unified_df <- hfa_encoding_df %>%
  ungroup() %>%
  filter(predictor == "max") %>%
  select(subject, electrode, epoch, perm_p_unified_fdr) %>%
  rename(max_unified_p  = perm_p_unified_fdr)

split_v_uni_max_df <- full_join(scatter_plot_r2_fdr_df, max_unified_df)

# filter to relevant conditions
split_v_uni_max_df <- split_v_uni_max_df %>%
  filter(max_unified_p < 0.05) %>%
  filter(sig != "Not Sig.") %>%
  filter((predictor == "self_var_payoff" & sig == "Advantageous") |
           (predictor == "other_var_payoff" & sig == "Disadvantageous"))

# save to cssv #
write_csv(split_v_uni_max_df, path(here(), "results", "unified_max_split_elecs.csv"))
```

```{r viz-max-uni-encoding}

pre_both_df <- split_v_uni_max_df %>%
  filter(epoch == "presentation") 

for(sub in unique(pre_both_df$subject)) {
  
  pre_both_sub_df <- pre_both_df %>%
    filter(subject == sub) 
  
  for(elec in unique(pre_both_sub_df$electrode)) {
    
    both_sig_sub_elec <- pre_both_sub_df %>%
      filter(electrode == elec) 
    
    brain_behave_elec <- all_brain_data_pres %>%
      filter(subject == sub & electrodes == elec)
    
    for(pred in unique(both_sig_sub_elec$predictor)){
      
     adv_plot <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
      adv_plot_max <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = max)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot_max <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = max)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
         
       print(plot( arrangeGrob(grobs = list(adv_plot,adv_plot_max, dis_plot, dis_plot_max), nrow = 2, ncol = 2)))

      
      
    }

  }
  
}

pre_both_df <- split_v_uni_max_df %>%
  filter(epoch == "pre-choice") 

for(sub in unique(pre_both_df$subject)) {
  
  pre_both_sub_df <- pre_both_df %>%
    filter(subject == sub) 
  
  for(elec in unique(pre_both_sub_df$electrode)) {
    
    both_sig_sub_elec <- pre_both_sub_df %>%
      filter(electrode == elec) 
    
    brain_behave_elec <- all_brain_data_pre_choice %>%
      filter(subject == sub & electrodes == elec)
    
    for(pred in unique(both_sig_sub_elec$predictor)){
      
     adv_plot <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
      adv_plot_max <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = max)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot_max <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = max)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
         
       print(plot( arrangeGrob(grobs = list(adv_plot,adv_plot_max, dis_plot, dis_plot_max), nrow = 2, ncol = 2)))

      
      
    }

  }
  
}

pre_both_df <- split_v_uni_max_df %>%
  filter(epoch == "post-choice") 

for(sub in unique(pre_both_df$subject)) {
  
  pre_both_sub_df <- pre_both_df %>%
    filter(subject == sub) 
  
  for(elec in unique(pre_both_sub_df$electrode)) {
    
    both_sig_sub_elec <- pre_both_sub_df %>%
      filter(electrode == elec) 
    
    brain_behave_elec <- all_brain_data_post_choice %>%
      filter(subject == sub & electrodes == elec)
    
    for(pred in unique(both_sig_sub_elec$predictor)){
      
     adv_plot <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
      adv_plot_max <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = max)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot_max <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = max)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
         
       print(plot( arrangeGrob(grobs = list(adv_plot,adv_plot_max, dis_plot, dis_plot_max), nrow = 2, ncol = 2)))

      
      
    }

  }
  
}

```

### Unified Min Encoding

```{r  unified-min}

min_unified_df <- hfa_encoding_df %>%
  ungroup() %>%
  filter(predictor == "min") %>%
  select(subject, electrode, epoch, perm_p_unified_fdr) %>%
  rename(min_unified_p  = perm_p_unified_fdr)

split_v_uni_min_df <- full_join(scatter_plot_r2_fdr_df, min_unified_df)

# filter to relevant conditions
split_v_uni_min_df <- split_v_uni_min_df %>%
  filter(min_unified_p < 0.05) %>%
  filter(sig != "Not Sig.") %>%
  filter((predictor == "other_var_payoff" & sig == "Advantageous") |
           (predictor == "dis_var_payoff" & sig == "Disadvantageous"))


```

```{r viz-min-uni-encoding}

pre_both_df <- split_v_uni_min_df %>%
  filter(epoch == "presentation") 

for(sub in unique(pre_both_df$subject)) {
  
  pre_both_sub_df <- pre_both_df %>%
    filter(subject == sub) 
  
  for(elec in unique(pre_both_sub_df$electrode)) {
    
    both_sig_sub_elec <- pre_both_sub_df %>%
      filter(electrode == elec) 
    
    brain_behave_elec <- all_brain_data_pres %>%
      filter(subject == sub & electrodes == elec)
    
    for(pred in unique(both_sig_sub_elec$predictor)){
      
     adv_plot <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
      adv_plot_min <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = min)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot_min <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("bin_"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("bin_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = min)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
         
       print(plot( arrangeGrob(grobs = list(adv_plot,adv_plot_min, dis_plot, dis_plot_min), nrow = 2, ncol = 2)))

      
      
    }

  }
  
}

pre_both_df <- split_v_uni_min_df %>%
  filter(epoch == "pre-choice") 

for(sub in unique(pre_both_df$subject)) {
  
  pre_both_sub_df <- pre_both_df %>%
    filter(subject == sub) 
  
  for(elec in unique(pre_both_sub_df$electrode)) {
    
    both_sig_sub_elec <- pre_both_sub_df %>%
      filter(electrode == elec) 
    
    brain_behave_elec <- all_brain_data_pre_choice %>%
      filter(subject == sub & electrodes == elec)
    
    for(pred in unique(both_sig_sub_elec$predictor)){
      
     adv_plot <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
      adv_plot_min <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = min)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot_min <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("pre"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("pre_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = min)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
         
       print(plot( arrangeGrob(grobs = list(adv_plot,adv_plot_min, dis_plot, dis_plot_min), nrow = 2, ncol = 2)))

      
      
    }

  }
  
}

pre_both_df <- split_v_uni_min_df %>%
  filter(epoch == "post-choice") 

for(sub in unique(pre_both_df$subject)) {
  
  pre_both_sub_df <- pre_both_df %>%
    filter(subject == sub) 
  
  for(elec in unique(pre_both_sub_df$electrode)) {
    
    both_sig_sub_elec <- pre_both_sub_df %>%
      filter(electrode == elec) 
    
    brain_behave_elec <- all_brain_data_post_choice %>%
      filter(subject == sub & electrodes == elec)
    
    for(pred in unique(both_sig_sub_elec$predictor)){
      
     adv_plot <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes_string(x = pred)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
      adv_plot_min <-  brain_behave_elec %>%
        filter(trial_type == "Advantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = min)) +
        geom_point(aes(y = HFA), color = "#5BA6D6") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white"), axis.title.x = element_blank()) +
        facet_wrap(~time, nrow = 1) + 
        scale_x_continuous(n.breaks = 3) +
        ggtitle(paste(sub, elec, sep = " "))
      
      dis_plot_min <-  brain_behave_elec %>%
        filter(trial_type == "Disadvantageous") %>%
        pivot_longer(cols = starts_with("post"), values_to = "HFA", names_to = "bin") %>%
        mutate(time = 50 * as.numeric(gsub("post_", "", bin))) %>%
        filter(time <= 1000) %>%
        ggplot(., aes(x = min)) +
        geom_point(aes(y = HFA), color = "#E4635C") +
        geom_smooth(aes(y = HFA), color = 'black', fill = 'grey', method = "lm", formula = 'y ~ x') +
        theme(panel.background = element_rect(fill = "white")) +
        scale_x_continuous(n.breaks = 3) +
        facet_wrap(~time, nrow = 1)
      
         
       print(plot( arrangeGrob(grobs = list(adv_plot,adv_plot_min, dis_plot, dis_plot_min), nrow = 2, ncol = 2)))

      
      
    }

  }
  
}

```


